---
title: "Comparative Analysis"
author: "Anon"
date: "Revised 2026-08-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NOTE

Identification has been renamed to "Find" tasks
Estimation has been renamed to "Lookup" tasks

## Data Cleaning

```{r libraryImportEtc}
library(plyr)
library(tidyverse)
library(readxl)
library(purrr)
library(lme4)
library(ggpubr)
library(emmeans)
library(glmmTMB)
library(robustlmm)
library(ggdist)
library(svglite)
```

```{r initialReadIn}
data <- read_csv("ThresholdData.csv")
answerKey <- read_xlsx("AnswerKeyThreshold.xlsx")

data.clean <- data |>
  filter(Finished == "TRUE") |>
  mutate(StartDate = as.Date(StartDate, "%m/%d/%y")) |>
  filter(StartDate >= ymd("2024-09-17")) |>
  select(-contains("Click"))
```

```{r dataCleaning}
list_questions = c("1", "2", "3", "4", "5", "6")
nonlist_questions = setdiff(names(answerKey), list_questions)

answerKey_list = as.list(answerKey)
answerKey_list[list_questions] = answerKey_list[list_questions] |>
  unlist() |>
  strsplit(",") |>
  map(as.numeric)

stopifnot(
  length(answerKey) == length(answerKey_list),
  !is.na(answerKey_list), 
  lengths(answerKey_list[list_questions]) == 4, 
  lengths(answerKey_list[nonlist_questions]) == 1
)

str(answerKey_list)

data.clean.answers = data.clean |>
  pivot_longer(
    cols = c(`ControlBIdeCurVal1_Page Submit`:SepSizeCEstTrend23), 
    names_to = "question",  
    values_to = "value"
  ) |>
  filter(!is.na(value)) |>
  mutate(
    type = if_else(str_detect(question, "_Page Submit"), "time", "Answer"),
    graph = case_when(
      str_detect(question, "ControlB") ~ "Control Band",
      str_detect(question, "ControlC") ~ "Control Color",
      str_detect(question, "IntSizeB") ~ "IntSize Band",
      str_detect(question, "IntSizeC") ~ "IntSize Color",
      str_detect(question, "SepSizeB") ~ "SepSize Band",
      str_detect(question, "SepSizeC") ~ "SepSize Color",
      str_detect(question, "Attention") ~ "AttentionCheck",
      .unmatched = "error"
    ),
    qtype = case_when(
      str_detect(question, "IdeCurVal") ~ "IdentCurVal",
      str_detect(question, "IdeTrend")  ~ "IdentTrend",
      str_detect(question, "EstCurVal") ~ "EstCurVal",
      str_detect(question, "EstTrend") ~ "EstTrend",
      str_detect(question, "Attention") ~ "AttentionCheck",
      .unmatched = "error"
    ),
    dist = str_extract(question, "[0-9]+")
  ) |>
  select(-question) |>
  pivot_wider(values_from = value, names_from = type) |>
  rename(question = qtype) |>
  mutate(
    dist = if_else(is.na(dist), "A", dist),
    Answer = strsplit(Answer, ",")
  )

data.clean.answers |>
  mutate(count = lengths(Answer)) |>
  summarise(min_n = min(count), max_n = max(count), .by = question) |>
  with(stopifnot(min_n == max_n, setequal(min_n, c(1, 3))))
```

```{r dataCleaning_answerscoded}
data.clean.answerscoded.raw = data.clean.answers |>
  mutate(
    actualAns = answerKey_list[dist],
    correctAns = map2(Answer, actualAns, intersect),
    ans_TF = lengths(correctAns) == lengths(Answer)
  ) |>
  rename(
    "QualitativeResponseWhy" = Q177
  ) |>
  select(StartDate:`Est Trend`, graph, question, dist, time, actualAns, ans_TF) |> 
  mutate(
    time = as.numeric(time),
    logTime = log(time)
  )  
```


```{r checkErrors}
data.clean.answerscoded.numCorrect <- data.clean.answerscoded.raw %>% 
  filter(dist != "A") %>% 
  group_by(ResponseId) %>% 
  mutate(NumCorrect = sum(ans_TF)) %>% 
  distinct(ResponseId, NumCorrect)

#Check for anyone outside of 2 standard deviations from the mean of number correct
cutoff <- mean(data.clean.answerscoded.numCorrect$NumCorrect) -
  2*sd(data.clean.answerscoded.numCorrect$NumCorrect)

data.clean.answerscoded.numCorrect.remove <- data.clean.answerscoded.numCorrect %>% 
  filter(NumCorrect < cutoff) %>% pull(ResponseId)

data.clean.answerscoded.AC <- data.clean.answerscoded.raw %>% 
  filter(dist == "A") %>% 
  filter(ans_TF == TRUE) %>% 
  pull(ResponseId)
```

```{r RemoveErrorCase}
data.clean.answerscoded <- data.clean.answerscoded.raw %>% 
  filter(!(ResponseId %in% data.clean.answerscoded.numCorrect.remove)) %>% 
  filter(ResponseId %in% data.clean.answerscoded.AC)

data.clean.answerscoded %>% dplyr::count(graph)
```

``` {r Demographics}
data.clean %>% dplyr::count(Age)
data.clean %>% dplyr::count(Gender)
data.clean %>% dplyr::count(Race)
data.clean %>% dplyr::count(`Hispanic/Latino`)
data.clean %>% dplyr::count(Q179)
```

```{r Outliers}
data.clean.answerscoded.outliers = data.clean.answerscoded |>
  filter(question != "AttentionCheck") |>
  mutate(
    .by = question,
    time_IQR = IQR(time),
    time_upper = quantile(time, probs = .75, na.rm = FALSE) + 1.5 * time_IQR,
    time_lower = quantile(time, probs = .25, na.rm = FALSE) - 1.5 * time_IQR,
    outlier = time > time_upper | time < time_lower
  ) |>
  # reorder designs and questions
  mutate(
    graph = graph |> fct_relevel(
      "Control Band", 
      "Control Color", 
      "IntSize Band", 
      "IntSize Color", 
      "SepSize Band", 
      "SepSize Color"
    ),
    question = question |> fct_relevel(
      "IdentCurVal", 
      "IdentTrend", 
      "EstCurVal",
      "EstTrend"
    )
  )
```


```{r}
overallModel <- 
  glmmTMB(logTime ~ graph + (1 | ResponseId), 
        dispformula = ~ graph, 
        family = glmmTMB::t_family, 
        data = data.clean.answerscoded.outliers %>% filter(outlier == FALSE),
        start = list(psi = log(4)),   # fix df to 4
        map = list(psi = factor(NA)))

summary(overallModel)
```

```{r}
models = data.clean.answerscoded.outliers |>
  
  # Remove outliers
  filter(outlier == FALSE) |>
  
  # Group by qurstions
  group_by(question) |>
  group_modify(\(data, groups) {
    model = glmmTMB(
        logTime ~ graph + (1 | ResponseId), 
        dispformula = ~ graph, 
        family = glmmTMB::t_family, 
        data = data,
        start = list(psi = log(4)),   # fix df to 4
        map = list(psi = factor(NA))
      )
    
    basemodel = glmmTMB(
        logTime ~ (1 | ResponseId), 
        family = glmmTMB::t_family, 
        data = data,
        start = list(psi = log(4)),   # fix df to 4
        map = list(psi = factor(NA))
      )

    # Estimate contrasts between all pairs of conditions with multiple 
    # comparison correction. We use "revpairwise" instead of "pairwise" to get
    # the same comparison direction as presented in the paper: 
    # (treatment - control) instead of (control - treatment). 
    estimates = model |>
      emmeans(~ graph) |> 
      contrast(method = "revpairwise") 
    
    # Get confidence intervals on estimates
    intervals = confint(estimates) |>
      # lmer and glmmTMB use different column names for intervals; normalize them
      rename(any_of(c(
        lower = "asymp.LCL", lower = "lower.CL", 
        upper = "asymp.UCL", upper = "upper.CL"
      )))
    
    # The use of tibble() + list() here creates a data frame with nested 
    # "list columns", which can contain complex objects like models or even
    # other data frames. This allows us to easily create a single dataframe
    # for visualizing specific things (like intervals) later using unnest().
    tibble(
      model = list(model), 
      basemodel = list(basemodel),
      estimates = list(estimates),
      intervals = list(intervals)
    )
  }) |>
  ungroup()

models
```

```{r Model Summary}
models$model[[1]]

# joint_tests(models$model[[1]])
# car::Anova(models$model[[1]])

models$estimates[[1]]
models$intervals[[1]]
```

```{r ModelPrint}
print(models$question[[1]])
models$model[[1]]
print(models$question[[2]])
models$model[[2]]
print(models$question[[3]])
models$model[[3]]
print(models$question[[4]])
models$model[[4]]

paste0("Estimate of ",  models$question[[1]], ": ", round(exp(2.76165), digits = 1))
paste0("Estimate of ",  models$question[[2]], ": ", round(exp(2.5002120), digits = 1))
paste0("Estimate of ",  models$question[[3]], ": ", round(exp(1.782080), digits = 1))
paste0("Estimate of ",  models$question[[4]], ": ", round(exp(1.89320), digits = 1))

```



```{r}
print(models$question[[1]])
anova(models$basemodel[[1]], models$model[[1]])
print(models$question[[2]])
anova(models$basemodel[[2]], models$model[[2]])
print(models$question[[3]])
anova(models$basemodel[[3]], models$model[[3]])
print(models$question[[4]])
anova(models$basemodel[[4]], models$model[[4]])

```

```{r Get Contrasts}
print(models$question[[1]])
models$estimates[[1]]
print(models$question[[2]])
models$estimates[[2]]
print(models$question[[3]])
models$estimates[[3]]
print(models$question[[4]])
models$estimates[[4]]
```

```{r}
percent_change = models |>
  # `models` uses nested list columns containing models and other data frames, 
  # so the first step is to ignore the other nested list columns and generate a 
  # single data frame with the confidence intervals from all the models
  select(-model, -basemodel, -estimates) |>
  unnest(intervals) |>

  # convert estimates of differences on log scale into percentage change
  mutate(across(c(estimate, lower, upper), expm1))

percent_change

percent_change_lim <- percent_change |>
  # focus only on contrasts against control
  filter(str_detect(contrast, "Control Band")) |>
  
  # re-order factor levels for presentation purposes
  mutate(  
    contrast = contrast |> 
      fct_relevel(
      "Control Color - Control Band",
      "IntSize Band - Control Band", 
      "IntSize Color - Control Band", 
      "SepSize Band - Control Band", 
      "SepSize Color - Control Band"
    ), 
    contrast = contrast |> 
      fct_recode(
        "Control Color - CB" = "Control Color - Control Band",
        "Int. Size Band - CB" = "IntSize Band - Control Band", 
        "Int. Size Color - CB" = "IntSize Color - Control Band", 
        "Sep. Size Band - CB" = "SepSize Band - Control Band", 
        "Sep. Size Color - CB" = "SepSize Color - Control Band"
    )
  )
```


```{r SetupTaskDatasets}
data.identCurVal <- data.clean.answerscoded %>% 
  filter(question == "IdentCurVal") %>% 
  mutate(dist = as.numeric(dist))

data.identTrend <- data.clean.answerscoded %>% 
  filter(question == "IdentTrend") %>% 
  mutate(dist = as.numeric(dist))

data.estCurVal <- data.clean.answerscoded %>% 
  filter(question == "EstCurVal") %>% 
  mutate(dist = as.numeric(dist))

data.estTrend <-  data.clean.answerscoded %>% 
  filter(question == "EstTrend") %>% 
  mutate(dist = as.numeric(dist))
```

## IDENTIFICATION CURRENT VALUE

Question Wording: Which machine has the highest output right now?

```{r Ident Current Val Outlier Check}
data.identCurVal.idOutliers <- data.identCurVal %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.identCurVal.idOutliers %>% count(outlier)

data.identCurVal.rmOutliers <- data.identCurVal.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```

## IDENTIFICATION TREND

Question Wording: Find 3 plots that have an overall output increasing over time. There may be more, but please select only 3.

```{r Ident Trend Outlier Check}
data.identTrend.idOutliers <- data.identTrend %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.identTrend.idOutliers %>% count(outlier)

data.identTrend.rmOutliers <- data.identTrend.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```

## ESTIMATION (LOOKUP) CURRENT VALUE

Question Wording: What is the output of Machine __ now?

```{r Est Cur Val Outlier Check}
data.estCurVal.idOutliers <- data.estCurVal %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.estCurVal.idOutliers %>% count(outlier)

data.estCurVal.rmOutliers <- data.estCurVal.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))

data.estCurVal %>% count(dist)
```

## ESTIMATION (LOOKUP) TREND

Question Wording: Is the overall output of Machine __ increasing, decreasing, or staying the same?

```{r Est Trend Outlier Check}
data.estTrend.idOutliers <- data.estTrend %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.estTrend.idOutliers %>% count(outlier)

data.estTrend.rmOutliers <- data.estTrend.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```

## SUMMARY STATS

```{r SummaryStats}
sumStats.identCurVal <- data.identCurVal.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.identTrend <- data.identTrend.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.estCurVal <- data.estCurVal.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.estTrend <- data.estTrend.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))
```

## Outlier Analysis


```{r Outlier Counts By Task & Participant}
data.outliers.identCurVal <- data.identCurVal.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "identCurVal")
  
data.outliers.identTrend <- data.identTrend.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "identTrend")

data.outliers.estCurVal <- data.estCurVal.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "estCurVal")
  
data.outliers.estTrend <- data.estTrend.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "estTrend")

data.outliers <- bind_rows(data.outliers.identCurVal, data.outliers.identTrend,
                              data.outliers.estCurVal, data.outliers.estTrend) %>% 
  mutate(question = as.numeric(question))

ggplot(data.outliers) + 
  geom_bar(aes(x = task)) + 
  theme_minimal() +
  ggtitle("Number of Outliers By Task")

ggplot(data.outliers) + 
  geom_bar(aes(x = ResponseId)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Participant")

ggplot(data.outliers) + 
  geom_bar(aes(x = dist)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Question")

ggplot(data.outliers) + 
  geom_bar(aes(x = dist)) + 
  facet_wrap(~ResponseId) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Question By Participant")
```

## Participant Analysis

```{r Participants}
data.identCurVal <- data.identCurVal %>% 
  mutate(task = "identCurVal")

data.identTrend <- data.identTrend %>% 
  mutate(task = "identTrend")

data.estCurVal <- data.estCurVal %>% 
  mutate(task = "estCurVal")

data.estTrend <- data.estTrend %>% 
  mutate(task = "estTrend")

data.participant <- bind_rows(data.identCurVal, data.identTrend,
                              data.estCurVal, data.estTrend) %>% 
  mutate(dist = as.numeric(dist))

participantMeans <- data.participant %>% 
  group_by(ResponseId) %>% 
  mutate(mean = mean(time),
         sd = sd(time)) %>%
  arrange(desc(mean)) %>% 
  ungroup()

participantMeans <- participantMeans %>% 
  distinct(ResponseId, .keep_all = T) %>% 
  arrange(desc(mean)) %>% 
  mutate(index = row_number()) %>% 
  full_join(participantMeans) %>% 
  arrange(ResponseId) %>% 
  fill(index, .direction = "down")

ggplot(data = participantMeans) + 
  geom_line(aes(x = dist, y = time, group = ResponseId)) +
  # scale_y_continuous(limits = c(NA, 45)) + 
  facet_wrap(~ResponseId) + 
  # geom_smooth(aes(x = question, y = time, group = ResponseId),
  #             se = F, method = "lm") + 
  geom_hline(aes(yintercept = mean), color = "blue")

ggplot(data = participantMeans) + 
  geom_line(aes(x = dist, y = time, group = ResponseId)) +
  scale_y_continuous(limits = c(NA, 60)) +
  facet_wrap(~ResponseId) + 
  # geom_smooth(aes(x = question, y = time, group = ResponseId),
  #             se = F, method = "lm") + 
  geom_hline(aes(yintercept = mean), color = "blue")

participantMeans.distinct <- participantMeans %>% 
  distinct(ResponseId, .keep_all = T)

ggplot(participantMeans.distinct) + 
  geom_histogram(aes(mean), binwidth = 2) +
  ggtitle("Participant Means")

# ggplot(data = participantMeans %>% filter(ResponseId %in% c("R_5hMwK9K1EG2F5Ey", "R_1G2JwQ0nmk1CHHk"))) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   facet_wrap(~ResponseId) + 
#   geom_hline(aes(yintercept = mean), color = "blue")
```

```{r ParticipantsByTasks}
# outliercutoffs <- data.outliers %>% distinct(task, question, upper)
# 
# participantMeans.cutoffs <- participantMeans %>% 
#   left_join(outliercutoffs, by = c("task", "question"))
# 
# ggplot(data = participantMeans.cutoffs) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   facet_wrap(~ResponseId) + 
#   scale_y_continuous(limits = c(NA, 100)) +
#   geom_line(aes(x = question, y = upper, group = ResponseId), color = "blue")
# 
# participantMeans.identCurVal <- participantMeans %>% 
#   filter(task == "identCurVal") %>% 
#   left_join(outliercutoffs, by = c("task", "question"))
# 
# ggplot(data = participantMeans.identCurVal) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   geom_point(aes(x = question, y = time, group = ResponseId)) +
#   geom_line(aes(x = question, y = upper), color = "blue") +
#   # scale_y_continuous(limits = c(NA, 100)) +
#   facet_wrap(~ResponseId) + 
#   ggtitle("Identification Current Value")
# 
# participantMeans.identTrend <- participantMeans %>% 
#   filter(task == "identTrend") %>% 
#   left_join(outliercutoffs, by = c("task", "question"))
# 
# ggplot(data = participantMeans.identTrend) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   geom_point(aes(x = question, y = time, group = ResponseId)) +
#   scale_y_continuous(limits = c(NA, 60)) +
#   facet_wrap(~ResponseId) + 
#   geom_hline(aes(yintercept = upper), color = "blue") + 
#   ggtitle("Identification Trend")
# 
# participantMeans.estCurVal <- participantMeans %>% 
#   filter(task == "estCurVal") %>% 
#   left_join(outliercutoffs, by = c("task", "question"))
# 
# ggplot(data = participantMeans.estCurVal) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   geom_point(aes(x = question, y = time, group = ResponseId)) +
#   scale_y_continuous(limits = c(NA, 60)) +
#   facet_wrap(~ResponseId) + 
#   geom_hline(aes(yintercept = upper), color = "blue") + 
#   ggtitle("Estimation Current Value")
# 
# participantMeans.estTrend <- participantMeans %>% 
#   filter(task == "estTrend") %>% 
#   left_join(outliercutoffs, by = c("task", "question"))
# 
# ggplot(data = participantMeans.estTrend) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   geom_point(aes(x = question, y = time, group = ResponseId)) +
#   scale_y_continuous(limits = c(NA, 60)) +
#   facet_wrap(~ResponseId) + 
#   geom_hline(aes(yintercept = upper), color = "blue") + 
#   ggtitle("Estimation Trend")

```



## ERROR ANALYSIS

```{r Error Descriptive}
#Ident Cur Val
with(data.identCurVal, table(graph, ans_TF))
#Ident Trend
with(data.identTrend, table(graph, ans_TF))
#Est Cur Val
with(data.estCurVal, table(graph, ans_TF))
#Est Trend
with(data.estTrend, table(graph, ans_TF))

#Ident Cur Val
with(data.identCurVal, table(dist, ans_TF))
#Ident Trend
with(data.identTrend, table(dist, ans_TF))
#Est Cur Val
with(data.estCurVal, table(dist, ans_TF))
#Est Trend
with(data.estTrend, table(dist, ans_TF))
```

```{r Error Count Plots}
ggplot(data = data.participant %>% mutate(ans = factor(ans_TF),
                                          graph = factor(graph, levels = c("Control Band", "Control Color", 
                                                                           "IntSize Band", "IntSize Color", 
                                                                           "SepSize Band", "SepSize Color"),
                                                         ordered = T))) + 
  geom_bar(aes(x = graph, group = ans, fill = ans), position = position_stack()) + 
  lemon::facet_rep_wrap(~task, repeat.tick.labels = T)

ggplot(data = data.participant %>% mutate(ans = factor(ans_TF))) + 
  geom_bar(aes(x = dist, group = ans, fill = ans), position = position_stack())
```


Modified error analysis following reviewer comments:

```{r}
error_models = data.clean.answerscoded.outliers |>
  group_by(question) |>
  group_modify(\(data, groups) {
    model = glmmTMB(
          ans_TF ~ graph + (1 | ResponseId),
          data = data,
          family = binomial(link = "logit"),
          prior = tribble(
            ~prior,           ~class,  ~coef,
            "cauchy(0, 10)",  "fixef", "(Intercept)", # control
            "cauchy(0, 2.5)", "fixef", ""             # differences from control
            )
          )
    basemodel = glmmTMB(
          ans_TF ~ (1 | ResponseId),
          data = data,
          family = binomial(link = "logit"),
          prior = tribble(
            ~prior,           ~class,  ~coef,
            "cauchy(0, 10)",  "fixef", "(Intercept)", # control
            "cauchy(0, 2.5)", "fixef", ""             # differences from control
            )
          )
    
    estimates = model |>
      emmeans(~ graph) |>
      contrast(method = "revpairwise")
    
    # unlike for the time models, we'll just look at the estimated proportion
    # of correct answers for an average participant in each graph type
    intervals = model |>
      emmeans(~ graph) |>
      confint(type = "response") |>
      rename(any_of(c(
        lower = "asymp.LCL", lower = "lower.CL",
        upper = "asymp.UCL", upper = "upper.CL"
      )))

    tibble(
      model = list(model), 
      basemodel = list(basemodel), 
      estimates = list(estimates),
      intervals = list(intervals)
    )
  }) |>
  ungroup()
```

```{r}
error_models
```

```{r Error Model Output}
error_models$model[[1]]
error_models$model[[2]]
error_models$model[[3]]
error_models$model[[4]]
```

```{r}
print(error_models$question[[1]])
anova(error_models$basemodel[[1]], error_models$model[[1]])
print(error_models$question[[2]])
anova(error_models$basemodel[[2]], error_models$model[[2]])
print(error_models$question[[3]])
anova(error_models$basemodel[[3]], error_models$model[[3]])
print(error_models$question[[4]])
anova(error_models$basemodel[[4]], error_models$model[[4]])
```

```{r IdentTrend Error Models}
summary(error_models$model[[2]])

error_models$estimates[[2]]
```


```{r error_plot}
data.clean.answerscoded.outliers |>
  summarise(
    incorrect = n() - sum(ans_TF), 
    prop_incorrect = incorrect/n(), 
    .by = c(question, graph)
  ) |>
  ggplot(aes(y = fct_rev(graph))) +
  geom_col(aes(x = prop_incorrect)) +
  geom_pointrange(
    aes(x = 1 - prob, xmin = 1 - upper, xmax = 1 - lower),
    position = position_dodge(width = 0.8),
    fill = NA,
    data = error_models |> select(question, intervals) |> unnest(intervals)
  ) +
  geom_text(aes(x = 0, label = incorrect), size = 3, hjust = 2) +
  facet_grid(rows = vars(question)) 
```

## LIKERT & QUALITATIVE ANALYSIS

```{r Likert}
data.clean.answerscoded %>% 
  count(`StandardBandRating`)

data.clean.answerscoded %>% 
  count(`StandardColorRating`)

data.clean.answerscoded %>% 
  count(`IntSizeBandRating`)

data.clean.answerscoded %>% 
  count(`IntSizeColorRating`)

data.clean.answerscoded %>% 
  count(`SepSizeBandRating`)

data.clean.answerscoded %>% 
  count(`SepSizeColorRating`)
```

```{r LikertCleaning}
data.clean.likert <- data.clean.answerscoded %>% 
  distinct(ResponseId, .keep_all = T) %>% 
  select(ResponseId, `StandardBandRating`, `StandardColorRating`, `IntSizeBandRating`, `IntSizeColorRating`,
         `SepSizeBandRating`, `SepSizeColorRating`) %>% 
  mutate(standBand = factor(`StandardBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         standBand = as.numeric(standBand),
         standColor = factor(`StandardColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         standColor = as.numeric(standColor),
         intSizeBand = factor(`IntSizeBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         intSizeBand = as.numeric(intSizeBand),
         intSizeColor = factor(`IntSizeColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         intSizeColor = as.numeric(intSizeColor),
         sepSizeBand = factor(`SepSizeBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         sepSizeBand = as.numeric(sepSizeBand),
         sepSizeColor = factor(`SepSizeColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         sepSizeColor = as.numeric(sepSizeColor)) %>% 
  select(-c(`StandardBandRating`, `StandardColorRating`, `IntSizeBandRating`, `IntSizeColorRating`,
         `SepSizeBandRating`, `SepSizeColorRating`)) %>% 
  pivot_longer(cols = c(standBand, standColor, intSizeBand, intSizeColor, sepSizeBand, sepSizeColor), 
               names_to = "graph", values_to = "likert") %>% 
  mutate(graph = factor(graph, levels = c("standBand", "standColor", "intSizeBand", 
                                          "intSizeColor", "sepSizeBand", "sepSizeColor"), ordered = T))
```

```{r LikertAnalysis}
anova.likert <- rstatix::anova_test(data = data.clean.likert, likert ~ graph, dv = likert, 
                                    wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.likert)

model.likert <- lme4::lmer(likert ~ graph + (1|ResponseId), data = data.clean.likert)
model.likert.null <- lme4::lmer(likert ~ (1|ResponseId), data = data.clean.likert)

anova(model.likert.null, model.likert)

summary(model.likert)

summary(multcomp::glht(model.likert, linfct=multcomp::mcp(graph="Tukey")))
```

```{r LikertGraph}
ggplot(data = data.clean.likert, aes(x = likert)) + 
  geom_histogram(binwidth = 1, color = "gray75") + 
  lemon::facet_rep_wrap(vars(graph), repeat.tick.labels = T) + 
  theme_minimal()

data.clean.likert <- data.clean.likert %>% 
  mutate(label = graph,
         label = fct_recode(label,  "Control Band" = "standBand", "Control Color" = "standColor",
                            "Int. Size Band" = "intSizeBand", 
                            "Int. Size Color" = "intSizeColor", 
                            "Sep. Size Band" = "sepSizeBand", 
                            "Sep. Size Color" = "sepSizeColor"))

data.clean.likert.factor <- data.clean.likert %>% 
  mutate(likert = factor(likert, ordered = T, labels = c("1", "2", "3", "4", "5")))

data.clean.likert.summarized <- data.clean.likert %>% 
  group_by(label) %>% 
  count(likert) %>% 
  mutate(percent = n/48)

library(RColorBrewer)
ggplot(data = data.clean.likert.factor, 
       aes(x = label, fill = reorder(likert, desc(likert)),
               group = reorder(likert, desc(likert)))) + 
  geom_bar(width = 0.7, position = "fill") +
  geom_text(aes(label = ..count..), stat = "count", 
            position = position_fill(vjust = 0.5), 
            size = 3) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0)),
                   breaks = c(seq(0, 1, by = .2)),
                   limits = c(0,1),
                   labels = scales::label_percent(),
                   name = "% of Responses") + 
  scale_x_discrete(expand = expansion(mult = c(0, 0)), limits = rev) + 
  scale_fill_manual(values = rev(brewer.pal(5, "Spectral")), guide = "none") + 
  coord_flip() + 
  theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
        aspect.ratio = 1/2.5,
        plot.margin = margin(t = 0,
                             r = 20, 
                             b = 15,
                             l = 10))
```

```{r}
source("ConfidenceIntervalHelperFunctions.R")

data.likert.means <- summarySEwithin(data = data.clean.likert, measurevar = "likert", 
                                       withinvars = "graph", idvar = "ResponseId")

ggplot(data.likert.means, aes(x=graph, y=likert, group=1)) +
  geom_errorbar(width=.1, aes(ymin=likert-ci, ymax=likert+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,6) +
  theme_minimal() + 
  ggtitle("Likert - Mean & CI")
```


## QUALITATIVE OUTPUT

```{r QualitativeResponseOutputs}
data.clean.qualitative <- data.clean.answerscoded %>% 
  select(ResponseId, QualitativeResponseWhy, Feedback) %>% 
  distinct(.keep_all = T)

# write_csv(data.clean.qualitative, "ComparativeQualitativeResponses_V2.csv")
```


## VISUALIZATIONS

```{r Percent Change Adjusted}
percent_change_lim_graph <- percent_change_lim %>% 
  add_row(question = "IdentCurVal", contrast = "Control Band (CB)", estimate = 0) %>% 
  add_row(question = "IdentTrend", contrast = "Control Band (CB)", estimate = 0) %>% 
  add_row(question = "EstCurVal", contrast = "Control Band (CB)", estimate = 0) %>% 
  add_row(question = "EstTrend", contrast = "Control Band (CB)", estimate = 0) %>% 
    mutate(
    question = question |> fct_relevel(
      "IdentCurVal", 
      "IdentTrend", 
      "EstCurVal",
      "EstTrend"),
    contrast = contrast |> 
      fct_relevel(
        "Control Band (CB)",
        "Control Color - CB",
        "Int. Size Band - CB",
        "Int. Size Color - CB", 
        "Sep. Size Band - CB", 
        "Sep. Size Color - CB"
    ))

ggplot(data = percent_change_lim_graph,
       aes(x = estimate, y = contrast)) +
  geom_vline(xintercept = 0, linewidth = 0.3, color = "gray50") +
  geom_errorbar(width=0, aes(xmin=lower, 
                             xmax=upper, 
                             color = question), 
                show.legend = F,
                linewidth = 1.6) +
  geom_point(aes(color = question), shape=21, size=3.6, 
             fill="white", show.legend = F) + 
  scale_color_manual(values = c("#317F9B","#13B6B9",
                                "#5F51B8","#9990E0")) +
  scale_x_continuous(limits = c(-0.4,0.4), expand = expansion(mult = c(0, 0)), 
                     name = "Percent Change from Control Estimate", 
                     labels = scales::percent) + 
  scale_y_discrete(limits=rev) + 
  facet_grid(rows = vars(question)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.7)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
                                   size = rel(1.7)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10),
        panel.spacing = unit(30, "pt"),
        strip.text.y = element_blank())

ggsave("GraphComparativeCIs_revision3.svg", width=7, height=7.3)
ggsave("GraphNonComparativeCIs_revision3.png", width=7, height=7.3, bg = "white")
```


```{r}
nrow(data.participant %>% distinct(ResponseId))

data.participant.error <- data.participant %>% 
  mutate(ans = factor(ans_TF),
         label = graph,
         label = fct_recode(label, 
                            "Int. Size Band" = "IntSize Band", "Int. Size Color" = "IntSize Color",
                            "Sep. Size Band" = "SepSize Band", "Sep. Size Color" = "SepSize Color"),
         label = factor(label, levels = rev(c("Control Band", "Control Color", 
                            "Int. Size Band", "Int. Size Color", 
                            "Sep. Size Band", "Sep. Size Color"))),
         task = fct_recode(task, 
                           "Ident. Current Value" = "identCurVal",
                           "Ident. Trend" = "identTrend",
                           "Lookup Current Value" = "estCurVal",
                           "Lookup Trend" = "estTrend"),
         task = factor(task, levels = c("Ident. Current Value", "Ident. Trend",
                       "Lookup Current Value","Lookup Trend"), ordered = T))

# ggplot(data = data.participant.error) + 
#   geom_bar(aes(x = label, group = ans, fill = ans), position = position_stack()) + 
#   geom_text(data = data.participant.error %>% filter(ans == T),
#             aes(x = label, group = ans, label = ..count..), stat = "count", 
#             position = position_fill(vjust = 0.5), 
#             size = 3, hjust = 0) + 
#   scale_fill_manual(labels = c("Incorrect", "Correct"),
#                     values = c("#EB919A", "#73BCE6"),
#                     name = "Answer Type") +
#   scale_y_continuous(expand = expansion(mult = c(0.01, 0)),
#                      breaks = c(0,10,20,30,40,47),
#                      labels = c("0","10","20","30","40","47"),
#                      name = "Number of Errors") +
#   scale_x_discrete(expand = expansion(mult = c(0.12, 0))) +
#   coord_flip() + 
#   facet_grid(rows = vars(task)) +
#   theme_minimal() +
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 0)),
#         axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 0, l = 0)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10),
#         panel.spacing = unit(12, "pt"),
#         legend.position = "bottom")

# ggsave("GraphComparativeErrors.svg", width=5, height=10)
# ggsave("GraphComparativeErrors.png", width=5, height=10, bg = "white")
```



```{r Error plots v2}
data.participant.error.summarize <- data.participant.error %>% 
  group_by(task, label, ans) %>% 
  count() %>% 
  ungroup() %>% 
  complete(task, label, ans, fill = list(n = 0))

ggplot(data = data.participant.error.summarize %>% filter(ans == F)) + 
  geom_col(aes(x = label, y = n), fill = "#EB919A") + 
  geom_text(aes(x = label, y = n, label =  n), 
            size = 5, hjust = -0.7) + 
  # scale_fill_manual(labels = c("Incorrect", "Correct"),
  #                   values = c("#EB919A", "#73BCE6"),
  #                   name = "Answer Type") +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0)),
                     breaks = c(0,20,40),
                     labels = c("0","20","40"),
                     name = "Number of Errors",
                     limits = c(0,47)) +
  scale_x_discrete(expand = expansion(mult = c(0.12, 0))) +
  coord_flip() + 
  facet_grid(rows = vars(task)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 0),
                                   size = rel(1.7)),
        axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 0, l = 0),
                                   size = rel(1.7)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10),
        legend.position = "bottom",
        panel.spacing = unit(30, "pt"),
        strip.text.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())

ggsave("GraphComparativeErrors_v3.svg", width=2.5, height=7.3)
ggsave("GraphComparativeErrors_v3.png", width=5, height=10, bg = "white")
```

```{r Likert Plot}
data.clean.likert.summarized <- data.clean.likert.factor %>% 
  group_by(label) %>% 
  count(likert) %>% 
  mutate(percent = n/47)

ggplot(data = data.clean.likert.summarized, 
       aes(x = label, y = percent, fill = reorder(likert, desc(likert)),
               group = reorder(likert, desc(likert)))) + 
  geom_col(width = 0.7, position = "fill") +
  geom_text(aes(label = n),
            color = ifelse((data.clean.likert.summarized$likert == "1" | data.clean.likert.summarized$likert == "5"),
                           "white", "black"),
            position = position_fill(vjust = 0.5), 
            size = 5.5) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0)),
                   breaks = c(seq(0, 1, by = .2)),
                   limits = c(0,1),
                   labels = scales::label_percent(),
                   name = "% of Responses") + 
  scale_x_discrete(expand = expansion(mult = c(0, 0)), limits = rev) + 
  scale_fill_manual(values = rev(brewer.pal(5, "RdYlBu")),
                    labels = rev(c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy")),
                    name = "Likert Rating") + 
  coord_flip() + 
  theme_minimal() + 
  guides(color = guide_legend(reverse=T)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0),
                                   size = rel(1.5)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.7)),
        legend.text = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.7)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
                                   size = rel(1.6)),
        aspect.ratio = 1/2.5,
        plot.margin = margin(t = 0,
                             r = 20, 
                             b = 15,
                             l = 10),
        legend.position = "bottom")

ggsave("GraphComparativeLikert.svg", width=10, height=5)
ggsave("GraphComparativeLikert.png", width=10, height=5, bg = "white")
```


```{r Summary Stats}
# means <- means %>% 
#   mutate(roundTime = sprintf(round(time, digits = 1), fmt = '%.1f'))
# 
# ggplot(data = means) +
#   geom_col(aes(y = time, x = graph, fill = task), show.legend = F) +
#   geom_errorbar(aes(x = graph, ymin=time-ci, ymax=time+ci), show.legend = F, width=0.5) +
#   geom_text(aes(x = graph, y = time-ci, label = roundTime),
#             color = "white",
#             size = 4, hjust = 1.4) + 
#   facet_grid(rows = vars(task)) +
#   scale_y_continuous(expand = expansion(mult = c(0.01, 0)),
#                      name = "Mean (seconds)",
#                      limits = c(0,20)) +
#   scale_x_discrete(expand = expansion(mult = c(0.12, 0))) +
#   scale_fill_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   coord_flip() + 
#   facet_grid(rows = vars(task)) +
#   theme_minimal() +
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 0),
#                                    size = rel(1.2)),
#         axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 0, l = 0),
#                                    size = rel(1.2)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10),
#         legend.position = "bottom",
#         panel.spacing = unit(30, "pt"),
#         panel.grid.minor = element_blank(),
#         panel.grid.major.x = element_blank())
# 
# ggsave("GraphComparativeMeans.svg", width=7, height=7.3)
```


## LEGACY CODE LEFT FOR TRANSPARENCY - following reviewer comments, code was overhauled

## IDENTIFICATION CURRENT VALUE

Question Wording: Which machine has the highest output right now?

```{r Ident Current Value Outlier Check - Orig}
# data.identCurVal.idOutliers <- data.identCurVal %>% 
#   mutate(IQR = IQR(time),
#          upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
#          lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
#          outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
#   ungroup()
# 
# data.identCurVal.idOutliers %>% count(outlier)
# 
# data.identCurVal.rmOutliers <- data.identCurVal.idOutliers %>% 
#   filter(outlier == 0) %>% 
#   mutate(logTime = log(time))
```


```{r IdentCurValBoxplot}
# ggboxplot(data.identCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
#                  title = "Identification Current Value")
# ggpar(ggboxplot(data.identCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
#                  title = "Identification Current Value"))
# 
# ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
#                  title = "Identification Current Value"), ylim = c(0,30))
# ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
#                  title = "Identification Current Value"), ylim = c(0,30))
```

```{r Ident Current Value CIs}
# source("ConfidenceIntervalHelperFunctions.R")
# 
# data.identCurVal.means <- summarySEwithin(data = data.identCurVal.rmOutliers, measurevar = "time", 
#                                        withinvars = "graph", idvar = "ResponseId") %>% 
#   mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
#                                           "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))
# 
# ggplot(data.identCurVal.means, aes(x=graph, y=time, group=1)) +
#   geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
#   geom_point(shape=21, size=3, fill="white") + 
#   ylim(0,25) +
#   theme_minimal() + 
#   ggtitle("Identification Current Value - Mean & CI")
# 
# ggplot(data.identCurVal.means, aes(x=graph, y=time, group=1)) +
#   geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
#   geom_point(shape=21, size=3, fill="white") + 
#   theme_minimal() +
#   coord_flip()
```

```{r IdentCurValAssumptions}
# data.identCurVal.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(time)
# 
# data.identCurVal.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(logTime)
# 
# ggplot(data.identCurVal.rmOutliers) + 
#   geom_histogram(aes(x = logTime))
# 
# ggqqplot(data.identCurVal.rmOutliers, "time", facet.by = "graph")
# ggqqplot(data.identCurVal.rmOutliers, "logTime", facet.by = "graph")
```

```{r IdentCurValStatTests}
# anova.identCurVal <- rstatix::anova_test(data = data.identCurVal.rmOutliers,
#                                          logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
# rstatix::get_anova_table(anova.identCurVal)
# 
# model.identCurVal <- lme4::lmer(logTime ~ graph + (1|ResponseId),
#                                 data = data.identCurVal.rmOutliers)
# summary(model.identCurVal)
# 
# model.identCurVal.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.identCurVal.rmOutliers,
#                                      REML=FALSE)
# model.identCurVal.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data.identCurVal.rmOutliers,
#                                      REML=FALSE)
# anova(model.identCurVal.null, model.identCurVal.test)
# 
# ggqqplot(resid(model.identCurVal))
# hist(resid(model.identCurVal))
# 
# shapiro.test(resid(model.identCurVal))
# shapiro.test(resid(model.identCurVal.test))
# 
# # coef(model.identCurVal.test)
# 
# summary(multcomp::glht(model.identCurVal, linfct=multcomp::mcp(graph="Tukey")))
```

```{r DensityPlots - Ident Current Value}
# ggplot(data = data.identCurVal.rmOutliers) + 
#   geom_density(aes(time, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Current Value")
# 
# ggplot(data = data.identCurVal.rmOutliers) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Current Value")
# 
# # ggplot(data = data.identCurVal.rmOutliers %>% filter(graph == "intSizeColor")) + 
# #   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
# #   theme_minimal() + 
# #   ggtitle("Identification Current Value")
```

## IDENTIFICATION TREND

Question Wording: Find 3 plots that have an overall output increasing over time. There may be more, but please select only 3.

```{r Ident Trend Outlier Check - Orig}
# data.identTrend.idOutliers <- data.identTrend %>% 
#   mutate(IQR = IQR(time),
#          upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
#          lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
#          outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
#   ungroup()
# 
# data.identTrend.idOutliers %>% count(outlier)
# 
# data.identTrend.rmOutliers <- data.identTrend.idOutliers %>% 
#   filter(outlier == 0) %>% 
#   mutate(logTime = log(time))
```

```{r IdentTrendBoxplot}
# ggboxplot(data.identCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
#                  title = "Identification Trend")
# ggpar(ggboxplot(data.identCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
#                  title = "Identification Trend"))
# 
# ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
#                  title = "Identification Trend"), ylim = c(0,30))
# ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
#                  title = "Identification Trend"), ylim = c(0,30))
```

```{r Ident Trend CIs}
# data.identTrend.means <- summarySEwithin(data = data.identTrend.rmOutliers, measurevar = "time", 
#                                        withinvars = "graph", idvar = "ResponseId") %>% 
#   mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
#                                           "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))
# 
# ggplot(data.identTrend.means, aes(x=graph, y=time, group=1)) +
#   geom_line() +
#   geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
#   geom_point(shape=21, size=3, fill="white") + 
#   ylim(0,20) +
#   theme_minimal() + 
#   ggtitle("Identification Trend - Mean & CI")
```

```{r DensityPlots - Ident Trend}
# ggplot(data = data.identTrend.rmOutliers) + 
#   geom_density(aes(time, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Trend")
# 
# ggplot(data = data.identTrend.rmOutliers) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Trend")
# 
# # ggplot(data = data.identTrend.rmOutliers %>% filter(graph == "intSize")) + 
# #   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
# #   theme_minimal() + 
# #   ggtitle("Identification Trend")
```

```{r IdentTrendAssumptions}
# data.identTrend.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(time)
# 
# data.identTrend.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(logTime)
# 
# ggqqplot(data.identTrend.rmOutliers, "time", facet.by = "graph")
# ggqqplot(data.identTrend.rmOutliers, "logTime", facet.by = "graph")
```

```{r IdentTrendStatTests}
# anova.identTrend <- rstatix::anova_test(data = data.identTrend.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
# rstatix::get_anova_table(anova.identTrend)
# 
# model.identTrend <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.identTrend.rmOutliers)
# summary(model.identTrend)
# 
# model.identTrend.null <- lme4::lmer(logTime ~ (1|ResponseId), 
#                                     data = data.identTrend.rmOutliers, REML=FALSE)
# model.identTrend.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), 
#                                     data = data.identTrend.rmOutliers, REML=FALSE)
# anova(model.identTrend.null, model.identTrend.test)
# 
# ggqqplot(resid(model.identTrend))
# hist(resid(model.identTrend))
# 
# shapiro.test(resid(model.identTrend))
# shapiro.test(resid(model.identTrend.test))
# 
# # coef(model.identCurVal.test)
# 
# summary(multcomp::glht(model.identTrend, linfct=multcomp::mcp(graph="Tukey")))
```

## ESTIMATION (LOOKUP) CURRENT VALUE

Question Wording: What is the output of Machine __ now?

```{r Est Cur Val Outlier Check - Orig}
# data.estCurVal.idOutliers <- data.estCurVal %>% 
#   mutate(IQR = IQR(time),
#          upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
#          lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
#          outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
#   ungroup()
# 
# data.estCurVal.idOutliers %>% count(outlier)
# 
# data.estCurVal.rmOutliers <- data.estCurVal.idOutliers %>% 
#   filter(outlier == 0) %>% 
#   mutate(logTime = log(time))
# 
# data.estCurVal %>% count(dist)
```

```{r}
# ggboxplot(data.estCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
#                  title = "Estimation (Lookup) Current Value")
# ggboxplot(data.estCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
#                  title = "Estimation (Lookup) Current Value")
# ggpar(ggboxplot(data.estCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
#                  title = "Estimation (Lookup) Current Value"), ylim = c(0,15))
# ggpar(ggboxplot(data.estCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
#                  title = "Estimation (Lookup) Current Value"), ylim = c(0,15))
```

```{r Est Cur Val CIs}
# data.estCurVal.means <- summarySEwithin(data = data.estCurVal.rmOutliers, measurevar = "time", 
#                                        withinvars = "graph", idvar = "ResponseId") %>% 
#   mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
#                                           "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))
# 
# ggplot(data.estCurVal.means, aes(x=graph, y=time, group=1)) +
#   geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
#   geom_point(shape=21, size=3, fill="white") + 
#   ylim(0,10) +
#   theme_minimal() + 
#   ggtitle("Estimation (Lookup) Current Value - Mean & CI")
```

```{r DensityPlots - Est Cur Val}
# ggplot(data = data.estCurVal.rmOutliers) + 
#   geom_density(aes(time, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Estimation Current Value")
# 
# ggplot(data = data.estCurVal.rmOutliers) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Estimation Current Value")
```

```{r}
# data.estCurVal.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(time)
# 
# data.estCurVal.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(logTime)
# 
# ggqqplot(data.estCurVal.rmOutliers, "time", facet.by = "graph")
# ggqqplot(data.estCurVal.rmOutliers, "logTime", facet.by = "graph")
```

```{r}
# anova.estCurVal <- rstatix::anova_test(data = data.estCurVal.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
# rstatix::get_anova_table(anova.estCurVal)
# 
# model.estCurVal <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estCurVal.rmOutliers)
# summary(model.estCurVal)
# 
# model.estCurVal.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.estCurVal.rmOutliers, REML=FALSE)
# model.estCurVal.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estCurVal.rmOutliers, REML=FALSE)
# anova(model.estCurVal.null, model.estCurVal.test)
# 
# ggqqplot(resid(model.estCurVal))
# hist(resid(model.estCurVal))
# 
# shapiro.test(resid(model.estCurVal))
# shapiro.test(resid(model.estCurVal.test))
# 
# # coef(model.estCurVal.test)
# 
# summary(multcomp::glht(model.estCurVal, linfct=multcomp::mcp(graph="Tukey")))
```

## ESTIMATION (LOOKUP) TREND

Question Wording: Is the overall output of Machine __ increasing, decreasing, or staying the same?

```{r EstTrend Outlier Check - Orig}
# data.estTrend.idOutliers <- data.estTrend %>% 
#   mutate(IQR = IQR(time),
#          upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
#          lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
#          outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
#   ungroup()
# 
# data.estTrend.idOutliers %>% count(outlier)
# 
# data.estTrend.rmOutliers <- data.estTrend.idOutliers %>% 
#   filter(outlier == 0) %>% 
#   mutate(logTime = log(time))
```

```{r}
# ggboxplot(data.estTrend.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
#                  title = "Estimation (Lookup) Trend")
# ggboxplot(data.estTrend.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
#                  title = "Estimation (Lookup) Trend")
# 
# ggpar(ggboxplot(data.estTrend.rmOutliers, x = "graph", y = "time", add = "point", 
#                  title = "Estimation (Lookup) Trend"), ylim = c(0, 15))
# ggpar(ggboxplot(data.estTrend.rmOutliers, x = "dist", y = "time", add = "point", 
#                  title = "Estimation (Lookup) Trend"), ylim = c(0, 15))
```

```{r EstTrend CIs}
# data.estTrend.means <- summarySEwithin(data = data.estTrend.rmOutliers, measurevar = "time", 
#                                        withinvars = "graph", idvar = "ResponseId") %>% 
#   mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
#                                           "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))
# 
# ggplot(data.estTrend.means, aes(x=graph, y=time, group=1)) +
#   geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
#   geom_point(shape=21, size=3, fill="white") + 
#   ylim(0,10) +
#   theme_minimal() + 
#   ggtitle("Estimation (Lookup) Trend - Mean & CI")
```

```{r DensityPlots - Est Trend}
# ggplot(data = data.estTrend.rmOutliers) + 
#   geom_density(aes(time, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Estimation Trend")
# 
# ggplot(data = data.estTrend.rmOutliers) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Estimation Trend")
```

```{r}
# data.estTrend.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(time)
# 
# data.estTrend.rmOutliers %>%
#   group_by(graph) %>%
#   rstatix::shapiro_test(logTime)
# 
# ggqqplot(data.estTrend.rmOutliers, "time", facet.by = "graph")
# ggqqplot(data.estTrend.rmOutliers, "logTime", facet.by = "graph")
```

```{r}
# anova.estTrend <- rstatix::anova_test(data = data.estTrend.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
# rstatix::get_anova_table(anova.estTrend)
# 
# model.estTrend <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estTrend.rmOutliers)
# summary(model.estTrend)
# 
# model.estTrend.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.estTrend.rmOutliers, REML=FALSE)
# model.estTrend.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estTrend.rmOutliers,
#                                   REML=FALSE, )
# anova(model.estTrend.null, model.estTrend.test)
# 
# ggqqplot(resid(model.estTrend))
# hist(resid(model.estTrend))
# 
# shapiro.test(resid(model.estTrend))
# shapiro.test(resid(model.estTrend.test))
# 
# # coef(model.estCurVal.test)
# 
# summary(multcomp::glht(model.estTrend, linfct=multcomp::mcp(graph="Tukey")))
```


## LEGACY ERROR ANALYSIS - replaced during review stage

```{r ErrorAnalysis IdentCurVal}
# data.identCurVal$ans <- factor(data.identCurVal$ans)
# data.identCurVal$ResponseId <- factor(data.identCurVal$ResponseId)
# 
# model.identCurVal.error.null <- lme4::glmer(ans ~ (1|ResponseId), 
#                                             data = data.identCurVal,
#                                             family = binomial(link = "logit"))
# model.identCurVal.error.test <- lme4::glmer(ans ~ graph + (1|ResponseId), 
#                                             data = data.identCurVal,
#                                             family = binomial(link = "logit"))
# 
# # model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
# #                                   family = binomial(link = "logit"))
# 
# anova(model.identCurVal.error.null, model.identCurVal.error.test)
# 
# summary(model.identCurVal.error.test)
# 
# summary(multcomp::glht(model.identCurVal.error.test, linfct=multcomp::mcp(graph="Tukey")))
```

```{r ErrorAnalysis IdentTrend}
# data.identTrend$ans <- factor(data.identTrend$ans)
# data.identTrend$ResponseId <- factor(data.identTrend$ResponseId)
# 
# model.identTrend.error.null <- lme4::glmer(ans ~ (1|ResponseId), 
#                                             data = data.identTrend,
#                                             family = binomial(link = "logit"))
# model.identTrend.error.test <- lme4::glmer(ans ~ graph + (1|ResponseId), 
#                                             data = data.identTrend,
#                                             family = binomial(link = "logit"))
# 
# # model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
# #                                   family = binomial(link = "logit"))
# 
# anova(model.identTrend.error.null, model.identTrend.error.test)
# 
# summary(model.identTrend.error.test)
# 
# summary(multcomp::glht(model.identTrend.error.test, linfct=multcomp::mcp(graph="Tukey")))
```

```{r ErrorAnalysis EstCurVal}
# data.estCurVal$ans <- factor(data.estCurVal$ans)
# data.estCurVal$ResponseId <- factor(data.estCurVal$ResponseId)
# 
# model.estCurVal.error.test <- lme4::glmer(ans ~ (1|ResponseId), 
#                                             data = data.estCurVal,
#                                             family = binomial(link = "logit"))
# model.estCurVal.error.null <- lme4::glmer(ans ~ graph + (1|ResponseId), 
#                                             data = data.estCurVal,
#                                             family = binomial(link = "logit"))
# 
# # model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
# #                                   family = binomial(link = "logit"))
# 
# anova(model.estCurVal.error.null, model.estCurVal.error.test)
```

```{r ErrorAnalysisCheck EstTrend}
# data.estTrend$ans <- factor(data.estTrend$ans)
# data.estTrend$ResponseId <- factor(data.estTrend$ResponseId)
# 
# model.estTrend.error.test <- lme4::glmer(ans ~ (1|ResponseId), data = data.estTrend,
#                                          family = binomial(link = "logit"))
# model.estTrend.error.null <- lme4::glmer(ans ~ graph + (1|ResponseId), data = data.estTrend,
#                                   family = binomial(link = "logit"))
# 
# # model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
# #                                   family = binomial(link = "logit"))
# 
# anova(model.estTrend.error.null, model.estTrend.error.test)
```

## LEGACY VISUALIZATIONS

```{r Confidence Interval Adjusted Plots}
# data.identCurVal.means <- data.identCurVal.means %>% 
#   mutate(meanTimeAdjBand = time - (data.identCurVal.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
#   mutate(meanTimeAdjColor = time - (data.identCurVal.means %>% filter(graph == "Control Color") 
#                                     %>% pull(time))) %>% 
#   mutate(meanTimeRelBand = time/(data.identCurVal.means %>% filter(graph == "Control Band") %>% pull(time)),
#          ciRelBand = ci/(data.identCurVal.means %>% filter(graph == "Control Band") %>% pull(time)),
#          meanTimeRelColor = time/(data.identCurVal.means %>% filter(graph == "Control Color") %>% pull(time)),
#          ciRelColor = ci/(data.identCurVal.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(task = "Ident. Current Value")
# 
# data.identTrend.means <- data.identTrend.means %>% 
#   mutate(meanTimeAdjBand = time - (data.identTrend.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
#   mutate(meanTimeAdjColor = time - (data.identTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(meanTimeRelBand = time/(data.identTrend.means %>% filter(graph == "Control Band") %>% pull(time)),
#          ciRelBand = ci/(data.identTrend.means %>% filter(graph == "Control Band") %>% pull(time)),
#          meanTimeRelColor = time/(data.identTrend.means %>% filter(graph == "Control Color") %>% pull(time)),
#          ciRelColor = ci/(data.identTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(task = "Ident. Trend")
# 
# data.estCurVal.means <- data.estCurVal.means %>% 
#   mutate(meanTimeAdjBand = time - (data.estCurVal.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
#   mutate(meanTimeAdjColor = time - (data.estCurVal.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(meanTimeRelBand = time/(data.estCurVal.means %>% filter(graph == "Control Band") %>% pull(time)),
#          ciRelBand = ci/(data.estCurVal.means %>% filter(graph == "Control Band") %>% pull(time)),
#          meanTimeRelColor = time/(data.estCurVal.means %>% filter(graph == "Control Color") %>% pull(time)),
#          ciRelColor = ci/(data.estCurVal.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(task = "Lookup Current Value")
# 
# data.estTrend.means <- data.estTrend.means %>% 
#   mutate(meanTimeAdjBand = time - (data.estTrend.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
#   mutate(meanTimeAdjColor = time - (data.estTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>%
#   mutate(meanTimeRelBand = time/(data.estTrend.means %>% filter(graph == "Control Band") %>% pull(time)),
#          ciRelBand = ci/(data.estTrend.means %>% filter(graph == "Control Band") %>% pull(time)),
#          meanTimeRelColor = time/(data.estTrend.means %>% filter(graph == "Control Color") %>% pull(time)),
#          ciRelColor = ci/(data.estTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
#   mutate(task = "Lookup Trend")
# 
# means <- bind_rows(data.identCurVal.means, data.identTrend.means,
#                    data.estCurVal.means, data.estTrend.means) %>% 
#   mutate(task = factor(task, levels = c("Ident. Current Value", "Ident. Trend",
#                        "Lookup Current Value","Lookup Trend"), ordered = T),
#          label = graph,
#          label = fct_recode(label, 
#                             "Int. Size Band" = "IntSize Band", "Int. Size Color" = "IntSize Color",
#                             "Sep. Size Band" = "SepSize Band", "Sep. Size Color" = "SepSize Color"),
#          label = factor(label, levels = rev(c("Control Band", "Control Color", 
#                             "Int. Size Band", "Int. Size Color", 
#                             "Sep. Size Band", "Sep. Size Color")),
#                         ordered =T))
# 
# ggplot(means, aes(x=label, y=meanTimeAdjBand)) +
#   geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
#   geom_hline(data = means %>% filter(graph == "Control Band"), 
#              aes(yintercept = meanTimeAdjBand + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_hline(data = means %>% filter(graph == "Control Band"),
#              aes(yintercept = meanTimeAdjBand - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_errorbar(width=0, aes(ymin=meanTimeAdjBand-ci, ymax=meanTimeAdjBand+ci, color = task), show.legend = F,
#                 linewidth = 1.6) +
#   geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
#   scale_y_continuous(limits = c(-5.5, 2), expand = expansion(mult = c(0, 0)), name = "Normalized Mean Time (seconds)") +
#   scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   theme_minimal() +
#   coord_flip() +
#   facet_grid(rows = vars(task)) + 
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
#                                    size = rel(1.7)),
#         axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
#                                    size = rel(1.7)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10),
#         panel.spacing = unit(30, "pt"),
#         strip.text.y = element_blank())
# 
# ggsave("GraphComparativeCIs_revision2.svg", width=7, height=7.3)
# ggsave("GraphComparativeCIs_revision2.png", width=7, height=7.3, bg = "white")
# 
# ggplot(means %>% filter(str_detect(graph, "Band")), aes(x=label, y=meanTimeAdjBand)) +
#   geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
#   geom_hline(data = means %>% filter(str_detect(graph, "Band")) %>% filter(graph == "Control Band"), 
#              aes(yintercept = meanTimeAdjBand + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_hline(data = means %>% filter(str_detect(graph, "Band")) %>% filter(graph == "Control Band"),
#              aes(yintercept = meanTimeAdjBand - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_errorbar(width=0, aes(ymin=meanTimeAdjBand-ci, ymax=meanTimeAdjBand+ci, color = task), show.legend = F,
#                 linewidth = 1.6) +
#   geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
#   scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   scale_y_continuous(limits = c(-6, 6), expand = expansion(mult = c(0, 0)), name = "Normalized Mean Time") +
#   theme_minimal() +
#   coord_flip() +
#   facet_grid(rows = vars(task)) + 
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
#         axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10))
# 
# # ggsave("GraphComparativeCIs_Band.svg", width=7, height=3.65)
# # ggsave("GraphComparativeCIs_Band.png", width=7, height=3.65, bg = "white")
# 
# ggplot(data = means %>% filter(str_detect(graph, "Color")),
#        aes(x=label, y=meanTimeAdjColor)) +
#   geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
#   geom_hline(data = means %>% filter(str_detect(graph, "Color")) %>% filter(graph == "Control Color"), 
#              aes(yintercept = meanTimeAdjColor + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_hline(data = means %>% filter(str_detect(graph, "Color")) %>% filter(graph == "Control Color"),
#              aes(yintercept = meanTimeAdjColor - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_errorbar(width=0, aes(ymin=meanTimeAdjColor-ci, ymax=meanTimeAdjColor+ci, color = task), show.legend = F,
#                 linewidth = 1.6) +
#   geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
#   scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   scale_y_continuous(limits = c(-6, 6), expand = expansion(mult = c(0, 0)), 
#                      name = "Normalized Mean Time") +
#   theme_minimal() +
#   coord_flip() +
#   facet_grid(rows = vars(task)) + 
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
#         axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10))
# 
# # ggsave("GraphComparativeCIs_Color.svg", width=7, height=3.65)
# # ggsave("GraphComparativeCIs_Color.png", width=7, height=3.65, bg = "white")
```

```{r Percent}
# ggplot(means, aes(x=label, y=meanTimeRelBand-1)) +
#   geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
#   geom_hline(data = means %>% filter(graph == "Control Band"),
#              aes(yintercept = meanTimeRelBand +ciRelBand-1), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_hline(data = means %>% filter(graph == "Control Band"),
#              aes(yintercept = meanTimeRelBand -ciRelBand-1), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_errorbar(width=0, aes(ymin=meanTimeRelBand-ciRelBand-1, 
#                              ymax=meanTimeRelBand+ciRelBand-1, color = task), show.legend = F,
#                 linewidth = 1.6) +
#   geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
#   scale_y_continuous(limits = c(-.35,.15), expand = expansion(mult = c(0, 0)),
#                      name = "Percent Change from Control Time", labels = scales::percent) +
#   scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   theme_minimal() +
#   coord_flip() +
#   facet_grid(rows = vars(task)) + 
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
#                                    size = rel(1.7)),
#         axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
#                                    size = rel(1.7)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10),
#         panel.spacing = unit(30, "pt"),
#         strip.text.y = element_blank())
# 
# ggsave("GraphComparativeCIs_percentnorm_revision2.svg", width=7, height=7.3)
# ggsave("GraphComparativeCIs_percentnorm_revision2.png", width=7, height=7.3, bg = "white")
# ```
# 
# ```{r}
# ggplot(means, aes(x=label, y=time)) +
#   geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
#   geom_hline(data = means %>% filter(graph == "Control Band"), 
#              aes(yintercept = time + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_hline(data = means %>% filter(graph == "Control Band"),
#              aes(yintercept = time - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
#   geom_errorbar(width=0, aes(ymin=time-ci, ymax=time+ci, color = task), show.legend = F,
#                 linewidth = 1.6) +
#   geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
#   scale_y_continuous(limits = c(NA,NA), expand = expansion(mult = c(0, 0)), name = "Mean Time (seconds)") +
#   scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
#   theme_minimal() +
#   coord_flip() +
#   facet_grid(rows = vars(task)) + 
#   theme(axis.title.y = element_blank(),
#         axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
#         axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
#                                    size = rel(1.7)),
#         axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
#                                    size = rel(1.7)),
#         plot.margin = margin(t = 10,
#                              r = 10, 
#                              b = 10,
#                              l = 10),
#         panel.spacing = unit(30, "pt"),
#         strip.text.y = element_blank())
# 
# ggsave("GraphComparativeCIs_meantime.svg", width=7, height=7.3)
# ggsave("GraphComparativeCIs_meantime.png", width=7, height=7.3, bg = "white")
```
