---
title: "Situated Visualization Threshold Analysis"
author: "Anon"
date: "2024-09-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NOTE

Identification has been renamed to "Find" tasks
Estimation has been renamed to "Lookup" tasks

## Data Cleaning

```{r libraryImportEtc}
library(plyr)
library(tidyverse)
library(readxl)
library(purrr)
library(ggpubr)

```

```{r initialReadIn}
data <- read_csv("ThresholdData.csv")

answerKey <- read_xlsx("AnswerKeyThreshold.xlsx")

data.clean <- data %>% 
  filter(Finished == "True") %>% 
  filter(StartDate >= ymd("2024-09-17")) %>% 
  select(-contains("Click"))

# view(data.clean %>% select(AttentionCheck))
```

```{r dataCleaning}
answerKey.lists <- answerKey %>% 
  mutate(`1`=list(reticulate::py_eval(`1`)),
         `2`=list(reticulate::py_eval(`2`)),
         `3`=list(reticulate::py_eval(`3`)),
         `4`=list(reticulate::py_eval(`4`)),
         `5`=list(reticulate::py_eval(`5`)),
         `6`=list(reticulate::py_eval(`6`)))

data.clean.answerscoded.raw <- data.clean %>% 
  pivot_longer(cols = c(`ControlBIdeCurVal1_Page Submit`:SepSizeCEstTrend23), 
               names_to = c("question"), 
               values_to = "value") %>% 
  filter(!is.na(value)) %>% 
  mutate(type = if_else(str_detect(question, "_Page Submit"), "time", "Answer"),
         graph = if_else(str_detect(question, "ControlB"), "Control Band",
                         if_else(str_detect(question, "ControlC"), "Control Color",
                         if_else(str_detect(question, "IntSizeB"), "IntSize Band",
                         if_else(str_detect(question, "IntSizeC"), "IntSize Color",
                         if_else(str_detect(question, "SepSizeB"), "SepSize Band",
                         if_else(str_detect(question, "SepSizeC"), "SepSize Color",
                         if_else(str_detect(question, "Attention"), "AttentionCheck", NA))))))),
         qtype = if_else((str_detect(question, "IdeCurVal") | 
                          str_detect(question, "IdentCurVal")) , "IdentCurVal",
                         if_else(str_detect(question, "IdeTrend"), "IdentTrend",
                         if_else(str_detect(question, "EstCurVal"), "EstCurVal",
                         if_else(str_detect(question, "EstTrend"), "EstTrend",
                         if_else(str_detect(question, "Attention"), "AttentionCheck", NA))))),
         dist = str_extract(question, "[0-9]+")) %>% 
  select(-question) %>% 
  pivot_wider(values_from = value, names_from = type) %>% 
  dplyr::rename(question = qtype) %>% 
  mutate(dist = if_else(is.na(dist),"A", dist)) %>% 
  pivot_wider(values_from = Answer, names_from = dist) %>% 
  rowwise() %>%
  #Make lists out of string
  mutate(`1`= list(as.list(as.numeric(unlist(str_extract_all(`1`, "[0-9]+"))))),
         `2`= list(as.list(as.numeric(unlist(str_extract_all(`2`, "[0-9]+"))))),
         `3`= list(as.list(as.numeric(unlist(str_extract_all(`3`, "[0-9]+"))))),
         `4`= list(as.list(as.numeric(unlist(str_extract_all(`4`, "[0-9]+"))))),
         `5`= list(as.list(as.numeric(unlist(str_extract_all(`5`, "[0-9]+"))))),
         `6`= list(as.list(as.numeric(unlist(str_extract_all(`6`, "[0-9]+")))))) %>% 
  ungroup() %>% 
  #Check multiple selection
  mutate(ans1 = imap(`1`, ~.x %in% answerKey.lists$`1`[[1]]),
         ans1 = map_dbl(ans1, ~ sum(.x, na.rm = TRUE)),
         ans2 = imap(`2`, ~.x %in% answerKey.lists$`2`[[1]]), 
         ans2 = map_dbl(ans2, ~ sum(.x, na.rm = TRUE)),
         ans3 = imap(`3`, ~.x %in% answerKey.lists$`3`[[1]]), 
         ans3 = map_dbl(ans3, ~ sum(.x, na.rm = TRUE)),
         ans4 = imap(`4`, ~.x %in% answerKey.lists$`4`[[1]]), 
         ans4 = map_dbl(ans4, ~ sum(.x, na.rm = TRUE)),
         ans5 = imap(`5`, ~.x %in% answerKey.lists$`5`[[1]]), 
         ans5 = map_dbl(ans5, ~ sum(.x, na.rm = TRUE)),
         ans6 = imap(`6`, ~.x %in% answerKey.lists$`6`[[1]]), 
         ans6 = map_dbl(ans6, ~ sum(.x, na.rm = TRUE))) %>%
  rowwise() %>% 
  mutate(ans1 = if_else(sum(anyNA(`1`)) >= 1, NA, ans1),
         ans2 = if_else(sum(anyNA(`2`)) >= 1, NA, ans2),
         ans3 = if_else(sum(anyNA(`3`)) >= 1, NA, ans3),
         ans4 = if_else(sum(anyNA(`4`)) >= 1, NA, ans4),
         ans5 = if_else(sum(anyNA(`5`)) >= 1, NA, ans5),
         ans6 = if_else(sum(anyNA(`6`)) >= 1, NA, ans6)) %>% 
  ungroup() %>% 
  #Check answers for the non-list options
  mutate(across(c(62:80),
                .fn = ~ .x == answerKey.lists[,cur_column()][[1]],
                .names = "ans{.col}")) %>% 
  #Transform to all right or not (T/F)
  mutate(across(c(81:86),
                .fn = ~ .x == 3)) %>% 
  pivot_longer(cols = c(81:105), 
               names_to = c("dist_ans"), 
               values_to = "ans_TF", values_drop_na = T) %>% 
  rowwise() %>% 
  mutate(`1` = toString(`1`),
         `1` = if_else(`1` == "NA", NA, `1`),
         `2` = toString(`2`),
         `2` = if_else(`2` == "NA", NA, `2`),
         `3` = toString(`3`),
         `3` = if_else(`3` == "NA", NA, `3`),
         `4` = toString(`4`),
         `4` = if_else(`4` == "NA", NA, `4`),
         `5` = toString(`5`),
         `5` = if_else(`5` == "NA", NA, `5`),
         `6` = toString(`6`),
         `6` = if_else(`6` == "NA", NA, `6`)) %>% 
  ungroup() %>% 
  pivot_longer(cols = c(56:80), 
               names_to = c("dist"), 
               values_to = "actualAns", values_drop_na = T) %>% 
  select(-dist_ans) %>% 
  select(StartDate:`Est Trend`, graph, question, dist, time, actualAns, ans_TF) %>% 
  mutate(time = as.numeric(time),
         ans = if_else(ans_TF == T, 1, 0)) %>% 
  rename("QualitativeResponseWhy" = Q177)

# data.clean.answerscoded.raw %>% count(graph)

data.clean.answerscoded.raw %>% count(dist)
```

```{r checkErrors}
data.clean.answerscoded.numCorrect <- data.clean.answerscoded.raw %>% 
  filter(dist != "A") %>% 
  group_by(ResponseId) %>% 
  mutate(NumCorrect = sum(ans_TF)) %>% 
  distinct(ResponseId, NumCorrect)

mean(data.clean.answerscoded.numCorrect$NumCorrect)
sd(data.clean.answerscoded.numCorrect$NumCorrect)

#Check for anyone outside of 2 standard deviations from the mean of number correct
cutoff <- mean(data.clean.answerscoded.numCorrect$NumCorrect) -
  2*sd(data.clean.answerscoded.numCorrect$NumCorrect)

data.clean.answerscoded.numCorrect$NumCorrect > cutoff

data.clean.answerscoded.numCorrect.remove <- data.clean.answerscoded.numCorrect %>% 
  filter(NumCorrect < cutoff) %>% pull(ResponseId)

data.clean.answerscoded.AC <- data.clean.answerscoded.raw %>% 
  filter(dist == "A") %>% 
  filter(actualAns == 16) %>% 
  pull(ResponseId)

median(as.numeric(data.clean$`Duration (in seconds)`))/60
```

``` {r Demographics}
data.clean %>% dplyr::count(Age)
data.clean %>% dplyr::count(Gender)
data.clean %>% dplyr::count(Race)
data.clean %>% dplyr::count(`Hispanic/Latino`)
data.clean %>% dplyr::count(Q179)
```

```{r RemoveErrorCase}
data.clean.answerscoded <- data.clean.answerscoded.raw %>% 
  filter(!(ResponseId %in% data.clean.answerscoded.numCorrect.remove)) %>% 
  filter(ResponseId %in% data.clean.answerscoded.AC)

data.clean.answerscoded %>% dplyr::count(graph)
```

```{r SetupTaskDatasets}
data.identCurVal <- data.clean.answerscoded %>% 
  filter(question == "IdentCurVal") %>% 
  mutate(dist = as.numeric(dist))

data.identTrend <- data.clean.answerscoded %>% 
  filter(question == "IdentTrend") %>% 
  mutate(dist = as.numeric(dist))

data.estCurVal <- data.clean.answerscoded %>% 
  filter(question == "EstCurVal") %>% 
  mutate(dist = as.numeric(dist))

data.estTrend <-  data.clean.answerscoded %>% 
  filter(question == "EstTrend") %>% 
  mutate(dist = as.numeric(dist))
```

## IDENTIFICATION CURRENT VALUE

Question Wording: Which machine has the highest output right now?

```{r Outlier Check}
data.identCurVal.idOutliers <- data.identCurVal %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.identCurVal.idOutliers %>% count(outlier)

data.identCurVal.rmOutliers <- data.identCurVal.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```


```{r IdentCurValBoxplot}
ggboxplot(data.identCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
                 title = "Identification Current Value")
ggpar(ggboxplot(data.identCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
                 title = "Identification Current Value"))

ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
                 title = "Identification Current Value"), ylim = c(0,30))
ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
                 title = "Identification Current Value"), ylim = c(0,30))
```

```{r CIs}
source("ConfidenceIntervalHelperFunctions.R")

data.identCurVal.means <- summarySEwithin(data = data.identCurVal.rmOutliers, measurevar = "time", 
                                       withinvars = "graph", idvar = "ResponseId") %>% 
  mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
                                          "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))

ggplot(data.identCurVal.means, aes(x=graph, y=time, group=1)) +
  geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,25) +
  theme_minimal() + 
  ggtitle("Identification Current Value - Mean & CI")

ggplot(data.identCurVal.means, aes(x=graph, y=time, group=1)) +
  geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  theme_minimal() +
  coord_flip()
```

```{r IdentCurValAssumptions}
data.identCurVal.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(time)

data.identCurVal.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(logTime)

ggplot(data.identCurVal.rmOutliers) + 
  geom_histogram(aes(x = logTime))

ggqqplot(data.identCurVal.rmOutliers, "time", facet.by = "graph")
ggqqplot(data.identCurVal.rmOutliers, "logTime", facet.by = "graph")
```

```{r IdentCurValStatTests}
anova.identCurVal <- rstatix::anova_test(data = data.identCurVal.rmOutliers,
                                         logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.identCurVal)

model.identCurVal <- lme4::lmer(logTime ~ graph + (1|ResponseId),
                                data = data.identCurVal.rmOutliers)
summary(model.identCurVal)

model.identCurVal.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.identCurVal.rmOutliers,
                                     REML=FALSE)
model.identCurVal.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data.identCurVal.rmOutliers,
                                     REML=FALSE)
anova(model.identCurVal.null, model.identCurVal.test)

ggqqplot(resid(model.identCurVal))
hist(resid(model.identCurVal))

shapiro.test(resid(model.identCurVal))
shapiro.test(resid(model.identCurVal.test))

# coef(model.identCurVal.test)

summary(multcomp::glht(model.identCurVal, linfct=multcomp::mcp(graph="Tukey")))
```

```{r DensityPlots - Ident Current Value}
ggplot(data = data.identCurVal.rmOutliers) + 
  geom_density(aes(time, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Identification Current Value")

ggplot(data = data.identCurVal.rmOutliers) + 
  geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Identification Current Value")

# ggplot(data = data.identCurVal.rmOutliers %>% filter(graph == "intSizeColor")) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Current Value")
```

## IDENTIFICATION TREND

Question Wording: Find 3 plots that have an overall output increasing over time. There may be more, but please select only 3.

```{r Outlier Check}
data.identTrend.idOutliers <- data.identTrend %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.identTrend.idOutliers %>% count(outlier)

data.identTrend.rmOutliers <- data.identTrend.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```

```{r IdentTrendBoxplot}
ggboxplot(data.identCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
                 title = "Identification Trend")
ggpar(ggboxplot(data.identCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
                 title = "Identification Trend"))

ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
                 title = "Identification Trend"), ylim = c(0,30))
ggpar(ggboxplot(data.identCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
                 title = "Identification Trend"), ylim = c(0,30))
```

```{r CIs}
data.identTrend.means <- summarySEwithin(data = data.identTrend.rmOutliers, measurevar = "time", 
                                       withinvars = "graph", idvar = "ResponseId") %>% 
  mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
                                          "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))

ggplot(data.identTrend.means, aes(x=graph, y=time, group=1)) +
  geom_line() +
  geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,20) +
  theme_minimal() + 
  ggtitle("Identification Trend - Mean & CI")
```

```{r DensityPlots - Ident Trend}
ggplot(data = data.identTrend.rmOutliers) + 
  geom_density(aes(time, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Identification Trend")

ggplot(data = data.identTrend.rmOutliers) + 
  geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Identification Trend")

# ggplot(data = data.identTrend.rmOutliers %>% filter(graph == "intSize")) + 
#   geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
#   theme_minimal() + 
#   ggtitle("Identification Trend")
```

```{r IdentTrendAssumptions}
data.identTrend.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(time)

data.identTrend.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(logTime)

ggqqplot(data.identTrend.rmOutliers, "time", facet.by = "graph")
ggqqplot(data.identTrend.rmOutliers, "logTime", facet.by = "graph")
```

```{r IdentTrendStatTests}
anova.identTrend <- rstatix::anova_test(data = data.identTrend.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.identTrend)

model.identTrend <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.identTrend.rmOutliers)
summary(model.identTrend)

model.identTrend.null <- lme4::lmer(logTime ~ (1|ResponseId), 
                                    data = data.identTrend.rmOutliers, REML=FALSE)
model.identTrend.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), 
                                    data = data.identTrend.rmOutliers, REML=FALSE)
anova(model.identTrend.null, model.identTrend.test)

ggqqplot(resid(model.identTrend))
hist(resid(model.identTrend))

shapiro.test(resid(model.identTrend))
shapiro.test(resid(model.identTrend.test))

# coef(model.identCurVal.test)

summary(multcomp::glht(model.identTrend, linfct=multcomp::mcp(graph="Tukey")))
```

## ESTIMATION (LOOKUP) CURRENT VALUE

Question Wording: What is the output of Machine __ now?

```{r Outlier Check}
data.estCurVal.idOutliers <- data.estCurVal %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.estCurVal.idOutliers %>% count(outlier)

data.estCurVal.rmOutliers <- data.estCurVal.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))

data.estCurVal %>% count(dist)
```

```{r}
ggboxplot(data.estCurVal.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
                 title = "Estimation (Lookup) Current Value")
ggboxplot(data.estCurVal.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
                 title = "Estimation (Lookup) Current Value")
ggpar(ggboxplot(data.estCurVal.rmOutliers, x = "graph", y = "time", add = "point", 
                 title = "Estimation (Lookup) Current Value"), ylim = c(0,15))
ggpar(ggboxplot(data.estCurVal.rmOutliers, x = "dist", y = "time", add = "point", 
                 title = "Estimation (Lookup) Current Value"), ylim = c(0,15))
```

```{r CIs}
data.estCurVal.means <- summarySEwithin(data = data.estCurVal.rmOutliers, measurevar = "time", 
                                       withinvars = "graph", idvar = "ResponseId") %>% 
  mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
                                          "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))

ggplot(data.estCurVal.means, aes(x=graph, y=time, group=1)) +
  geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,10) +
  theme_minimal() + 
  ggtitle("Estimation (Lookup) Current Value - Mean & CI")
```

```{r DensityPlots - Est Cur Val}
ggplot(data = data.estCurVal.rmOutliers) + 
  geom_density(aes(time, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Estimation Current Value")

ggplot(data = data.estCurVal.rmOutliers) + 
  geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Estimation Current Value")
```

```{r}
data.estCurVal.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(time)

data.estCurVal.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(logTime)

ggqqplot(data.estCurVal.rmOutliers, "time", facet.by = "graph")
ggqqplot(data.estCurVal.rmOutliers, "logTime", facet.by = "graph")
```

```{r}
anova.estCurVal <- rstatix::anova_test(data = data.estCurVal.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.estCurVal)

model.estCurVal <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estCurVal.rmOutliers)
summary(model.estCurVal)

model.estCurVal.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.estCurVal.rmOutliers, REML=FALSE)
model.estCurVal.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estCurVal.rmOutliers, REML=FALSE)
anova(model.estCurVal.null, model.estCurVal.test)

ggqqplot(resid(model.estCurVal))
hist(resid(model.estCurVal))

shapiro.test(resid(model.estCurVal))
shapiro.test(resid(model.estCurVal.test))

# coef(model.estCurVal.test)

summary(multcomp::glht(model.estCurVal, linfct=multcomp::mcp(graph="Tukey")))
```

## ESTIMATION (LOOKUP) TREND

Question Wording: Is the overall output of Machine __ increasing, decreasing, or staying the same?

```{r Outlier Check}
data.estTrend.idOutliers <- data.estTrend %>% 
  mutate(IQR = IQR(time),
         upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,
         lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR,
         outlier = if_else((time > upper | time < lower), 1, 0)) %>% 
  ungroup()

data.estTrend.idOutliers %>% count(outlier)

data.estTrend.rmOutliers <- data.estTrend.idOutliers %>% 
  filter(outlier == 0) %>% 
  mutate(logTime = log(time))
```

```{r}
ggboxplot(data.estTrend.idOutliers, x = "graph", y = "time", add = "point", color = "outlier",
                 title = "Estimation (Lookup) Trend")
ggboxplot(data.estTrend.idOutliers, x = "dist", y = "time", add = "point", color = "outlier",
                 title = "Estimation (Lookup) Trend")

ggpar(ggboxplot(data.estTrend.rmOutliers, x = "graph", y = "time", add = "point", 
                 title = "Estimation (Lookup) Trend"), ylim = c(0, 15))
ggpar(ggboxplot(data.estTrend.rmOutliers, x = "dist", y = "time", add = "point", 
                 title = "Estimation (Lookup) Trend"), ylim = c(0, 15))
```

```{r CIs}
data.estTrend.means <- summarySEwithin(data = data.estTrend.rmOutliers, measurevar = "time", 
                                       withinvars = "graph", idvar = "ResponseId") %>% 
  mutate(graph = factor(graph, levels = c("Control Band", "Control Color", "IntSize Band",
                                          "IntSize Color", "SepSize Band", "SepSize Color"), ordered = T))

ggplot(data.estTrend.means, aes(x=graph, y=time, group=1)) +
  geom_errorbar(width=.1, aes(ymin=time-ci, ymax=time+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,10) +
  theme_minimal() + 
  ggtitle("Estimation (Lookup) Trend - Mean & CI")
```

```{r DensityPlots - Est Trend}
ggplot(data = data.estTrend.rmOutliers) + 
  geom_density(aes(time, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Estimation Trend")

ggplot(data = data.estTrend.rmOutliers) + 
  geom_density(aes(logTime, fill = graph), alpha = 0.5) + 
  theme_minimal() + 
  ggtitle("Estimation Trend")
```

```{r}
data.estTrend.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(time)

data.estTrend.rmOutliers %>%
  group_by(graph) %>%
  rstatix::shapiro_test(logTime)

ggqqplot(data.estTrend.rmOutliers, "time", facet.by = "graph")
ggqqplot(data.estTrend.rmOutliers, "logTime", facet.by = "graph")
```

```{r}
anova.estTrend <- rstatix::anova_test(data = data.estTrend.rmOutliers, logTime ~ graph, dv = logTime, wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.estTrend)

model.estTrend <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estTrend.rmOutliers)
summary(model.estTrend)

model.estTrend.null <- lme4::lmer(logTime ~ (1|ResponseId), data = data.estTrend.rmOutliers, REML=FALSE)
model.estTrend.test <- lme4::lmer(logTime ~ graph + (1|ResponseId), data = data.estTrend.rmOutliers,
                                  REML=FALSE, )
anova(model.estTrend.null, model.estTrend.test)

ggqqplot(resid(model.estTrend))
hist(resid(model.estTrend))

shapiro.test(resid(model.estTrend))
shapiro.test(resid(model.estTrend.test))

# coef(model.estCurVal.test)

summary(multcomp::glht(model.estTrend, linfct=multcomp::mcp(graph="Tukey")))
```

## SUMMARY STATS

```{r SummaryStats}
sumStats.identCurVal <- data.identCurVal.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.identTrend <- data.identTrend.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.estCurVal <- data.estCurVal.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))

sumStats.estTrend <- data.estTrend.rmOutliers %>% 
  group_by(graph) %>% 
  summarise(mean = mean(time), sd = sd(time))
```


## ERROR ANALYSIS

```{r Error Descriptive}
#Ident Cur Val
with(data.identCurVal, table(graph, ans_TF))
#Ident Trend
with(data.identTrend, table(graph, ans_TF))
#Est Cur Val
with(data.estCurVal, table(graph, ans_TF))
#Est Trend
with(data.estTrend, table(graph, ans_TF))

#Ident Cur Val
with(data.identCurVal, table(dist, ans_TF))
#Ident Trend
with(data.identTrend, table(dist, ans_TF))
#Est Cur Val
with(data.estCurVal, table(dist, ans_TF))
#Est Trend
with(data.estTrend, table(dist, ans_TF))
```

```{r Error Count Plots}
ggplot(data = data.participant %>% mutate(ans = factor(ans_TF),
                                          graph = factor(graph, levels = c("Control Band", "Control Color", 
                                                                           "IntSize Band", "IntSize Color", 
                                                                           "SepSize Band", "SepSize Color"),
                                                         ordered = T))) + 
  geom_bar(aes(x = graph, group = ans, fill = ans), position = position_stack()) + 
  lemon::facet_rep_wrap(~task, repeat.tick.labels = T)

ggplot(data = data.participant %>% mutate(ans = factor(ans))) + 
  geom_bar(aes(x = dist, group = ans, fill = ans), position = position_stack())
```

```{r ErrorAnalysis IdentCurVal}
data.identCurVal$ans <- factor(data.identCurVal$ans)
data.identCurVal$ResponseId <- factor(data.identCurVal$ResponseId)

model.identCurVal.error.null <- lme4::glmer(ans ~ (1|ResponseId), 
                                            data = data.identCurVal,
                                            family = binomial(link = "logit"))
model.identCurVal.error.test <- lme4::glmer(ans ~ graph + (1|ResponseId), 
                                            data = data.identCurVal,
                                            family = binomial(link = "logit"))

# model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
#                                   family = binomial(link = "logit"))

anova(model.identCurVal.error.null, model.identCurVal.error.test)

summary(model.identCurVal.error.test)

summary(multcomp::glht(model.identCurVal.error.test, linfct=multcomp::mcp(graph="Tukey")))
```

```{r ErrorAnalysis IdentTrend}
data.identTrend$ans <- factor(data.identTrend$ans)
data.identTrend$ResponseId <- factor(data.identTrend$ResponseId)

model.identTrend.error.null <- lme4::glmer(ans ~ (1|ResponseId), 
                                            data = data.identTrend,
                                            family = binomial(link = "logit"))
model.identTrend.error.test <- lme4::glmer(ans ~ graph + (1|ResponseId), 
                                            data = data.identTrend,
                                            family = binomial(link = "logit"))

# model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
#                                   family = binomial(link = "logit"))

anova(model.identTrend.error.null, model.identTrend.error.test)

summary(model.identTrend.error.test)

summary(multcomp::glht(model.identTrend.error.test, linfct=multcomp::mcp(graph="Tukey")))
```

```{r ErrorAnalysis EstCurVal}
data.estCurVal$ans <- factor(data.estCurVal$ans)
data.estCurVal$ResponseId <- factor(data.estCurVal$ResponseId)

model.estCurVal.error.test <- lme4::glmer(ans ~ (1|ResponseId), 
                                            data = data.estCurVal,
                                            family = binomial(link = "logit"))
model.estCurVal.error.null <- lme4::glmer(ans ~ graph + (1|ResponseId), 
                                            data = data.estCurVal,
                                            family = binomial(link = "logit"))

# model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
#                                   family = binomial(link = "logit"))

anova(model.estCurVal.error.null, model.estCurVal.error.test)
```

```{r ErrorAnalysisCheck EstTrend}
data.estTrend$ans <- factor(data.estTrend$ans)
data.estTrend$ResponseId <- factor(data.estTrend$ResponseId)

model.estTrend.error.test <- lme4::glmer(ans ~ (1|ResponseId), data = data.estTrend,
                                         family = binomial(link = "logit"))
model.estTrend.error.null <- lme4::glmer(ans ~ graph + (1|ResponseId), data = data.estTrend,
                                  family = binomial(link = "logit"))

# model.estTrend.error.trial <- lme4::glmer(ans ~ graph + (1|question) + (1|ResponseId), data = data.estTrend,
#                                   family = binomial(link = "logit"))

anova(model.estTrend.error.null, model.estTrend.error.test)
```


## LIKERT & QUALITATIVE ANALYSIS

```{r Likert}
data.clean.answerscoded %>% 
  count(`StandardBandRating`)

data.clean.answerscoded %>% 
  count(`StandardColorRating`)

data.clean.answerscoded %>% 
  count(`IntSizeBandRating`)

data.clean.answerscoded %>% 
  count(`IntSizeColorRating`)

data.clean.answerscoded %>% 
  count(`SepSizeBandRating`)

data.clean.answerscoded %>% 
  count(`SepSizeColorRating`)
```

```{r LikertCleaning}
data.clean.likert <- data.clean.answerscoded %>% 
  distinct(ResponseId, .keep_all = T) %>% 
  select(ResponseId, `StandardBandRating`, `StandardColorRating`, `IntSizeBandRating`, `IntSizeColorRating`,
         `SepSizeBandRating`, `SepSizeColorRating`) %>% 
  mutate(standBand = factor(`StandardBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         standBand = as.numeric(standBand),
         standColor = factor(`StandardColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         standColor = as.numeric(standColor),
         intSizeBand = factor(`IntSizeBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         intSizeBand = as.numeric(intSizeBand),
         intSizeColor = factor(`IntSizeColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         intSizeColor = as.numeric(intSizeColor),
         sepSizeBand = factor(`SepSizeBandRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         sepSizeBand = as.numeric(sepSizeBand),
         sepSizeColor = factor(`SepSizeColorRating`, levels = c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy"), ordered = T),
         sepSizeColor = as.numeric(sepSizeColor)) %>% 
  select(-c(`StandardBandRating`, `StandardColorRating`, `IntSizeBandRating`, `IntSizeColorRating`,
         `SepSizeBandRating`, `SepSizeColorRating`)) %>% 
  pivot_longer(cols = c(standBand, standColor, intSizeBand, intSizeColor, sepSizeBand, sepSizeColor), 
               names_to = "graph", values_to = "likert") %>% 
  mutate(graph = factor(graph, levels = c("standBand", "standColor", "intSizeBand", 
                                          "intSizeColor", "sepSizeBand", "sepSizeColor"), ordered = T))
```

```{r LikertAnalysis}
anova.likert <- rstatix::anova_test(data = data.clean.likert, likert ~ graph, dv = likert, 
                                    wid = ResponseId, within = graph)
rstatix::get_anova_table(anova.likert)

model.likert <- lme4::lmer(likert ~ graph + (1|ResponseId), data = data.clean.likert)
model.likert.null <- lme4::lmer(likert ~ (1|ResponseId), data = data.clean.likert)

anova(model.likert.null, model.likert)

summary(model.likert)

summary(multcomp::glht(model.likert, linfct=multcomp::mcp(graph="Tukey")))
```

```{r LikertGraph}
ggplot(data = data.clean.likert, aes(x = likert)) + 
  geom_histogram(binwidth = 1, color = "gray75") + 
  lemon::facet_rep_wrap(vars(graph), repeat.tick.labels = T) + 
  theme_minimal()

data.clean.likert <- data.clean.likert %>% 
  mutate(label = graph,
         label = fct_recode(label,  "Control Band" = "standBand", "Control Color" = "standColor",
                            "Int. Size Band" = "intSizeBand", 
                            "Int. Size Color" = "intSizeColor", 
                            "Sep. Size Band" = "sepSizeBand", 
                            "Sep. Size Color" = "sepSizeColor"))

data.clean.likert.factor <- data.clean.likert %>% 
  mutate(likert = factor(likert, ordered = T, labels = c("1", "2", "3", "4", "5")))

data.clean.likert.summarized <- data.clean.likert %>% 
  group_by(label) %>% 
  count(likert) %>% 
  mutate(percent = n/48)

library(RColorBrewer)
ggplot(data = data.clean.likert.factor, 
       aes(x = label, fill = reorder(likert, desc(likert)),
               group = reorder(likert, desc(likert)))) + 
  geom_bar(width = 0.7, position = "fill") +
  geom_text(aes(label = ..count..), stat = "count", 
            position = position_fill(vjust = 0.5), 
            size = 3) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0)),
                   breaks = c(seq(0, 1, by = .2)),
                   limits = c(0,1),
                   labels = scales::label_percent(),
                   name = "% of Responses") + 
  scale_x_discrete(expand = expansion(mult = c(0, 0)), limits = rev) + 
  scale_fill_manual(values = rev(brewer.pal(5, "Spectral")), guide = "none") + 
  coord_flip() + 
  theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
        aspect.ratio = 1/2.5,
        plot.margin = margin(t = 0,
                             r = 20, 
                             b = 15,
                             l = 10))
```

```{r}
data.likert.means <- summarySEwithin(data = data.clean.likert, measurevar = "likert", 
                                       withinvars = "graph", idvar = "ResponseId")

ggplot(data.likert.means, aes(x=graph, y=likert, group=1)) +
  geom_errorbar(width=.1, aes(ymin=likert-ci, ymax=likert+ci)) +
  geom_point(shape=21, size=3, fill="white") + 
  ylim(0,6) +
  theme_minimal() + 
  ggtitle("Likert - Mean & CI")
```


## QUALITATIVE OUTPUT

```{r QualitativeResponseOutputs}
data.clean.qualitative <- data.clean.answerscoded %>% 
  select(ResponseId, QualitativeResponseWhy, Feedback) %>% 
  distinct(.keep_all = T)

# write_csv(data.clean.qualitative, "ComparativeQualitativeResponses.csv")
```

## Outlier Analysis


```{r Outlier Counts By Task & Participant}
data.outliers.identCurVal <- data.identCurVal.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "identCurVal")
  
data.outliers.identTrend <- data.identTrend.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "identTrend")

data.outliers.estCurVal <- data.estCurVal.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "estCurVal")
  
data.outliers.estTrend <- data.estTrend.idOutliers %>% 
  filter(outlier == 1) %>% 
  mutate(task = "estTrend")

data.outliers <- bind_rows(data.outliers.identCurVal, data.outliers.identTrend,
                              data.outliers.estCurVal, data.outliers.estTrend) %>% 
  mutate(question = as.numeric(question))

ggplot(data.outliers) + 
  geom_bar(aes(x = task)) + 
  theme_minimal() +
  ggtitle("Number of Outliers By Task")

ggplot(data.outliers) + 
  geom_bar(aes(x = ResponseId)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Participant")

ggplot(data.outliers) + 
  geom_bar(aes(x = dist)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Question")

ggplot(data.outliers) + 
  geom_bar(aes(x = dist)) + 
  facet_wrap(~ResponseId) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  ggtitle("Number of Outliers By Question By Participant")
```



## Participant Analysis


```{r Participants}
data.identCurVal <- data.identCurVal %>% 
  mutate(task = "identCurVal")

data.identTrend <- data.identTrend %>% 
  mutate(task = "identTrend")

data.estCurVal <- data.estCurVal %>% 
  mutate(task = "estCurVal")

data.estTrend <- data.estTrend %>% 
  mutate(task = "estTrend")

data.participant <- bind_rows(data.identCurVal, data.identTrend,
                              data.estCurVal, data.estTrend) %>% 
  mutate(dist = as.numeric(dist))

participantMeans <- data.participant %>% 
  group_by(ResponseId) %>% 
  mutate(mean = mean(time),
         sd = sd(time)) %>%
  arrange(desc(mean)) %>% 
  ungroup()

participantMeans <- participantMeans %>% 
  distinct(ResponseId, .keep_all = T) %>% 
  arrange(desc(mean)) %>% 
  mutate(index = row_number()) %>% 
  full_join(participantMeans) %>% 
  arrange(ResponseId) %>% 
  fill(index, .direction = "down")

ggplot(data = participantMeans) + 
  geom_line(aes(x = dist, y = time, group = ResponseId)) +
  # scale_y_continuous(limits = c(NA, 45)) + 
  facet_wrap(~ResponseId) + 
  # geom_smooth(aes(x = question, y = time, group = ResponseId),
  #             se = F, method = "lm") + 
  geom_hline(aes(yintercept = mean), color = "blue")

ggplot(data = participantMeans) + 
  geom_line(aes(x = dist, y = time, group = ResponseId)) +
  scale_y_continuous(limits = c(NA, 60)) +
  facet_wrap(~ResponseId) + 
  # geom_smooth(aes(x = question, y = time, group = ResponseId),
  #             se = F, method = "lm") + 
  geom_hline(aes(yintercept = mean), color = "blue")

participantMeans.distinct <- participantMeans %>% 
  distinct(ResponseId, .keep_all = T)

ggplot(participantMeans.distinct) + 
  geom_histogram(aes(mean), binwidth = 2) +
  ggtitle("Participant Means")

# ggplot(data = participantMeans %>% filter(ResponseId %in% c("R_5hMwK9K1EG2F5Ey", "R_1G2JwQ0nmk1CHHk"))) + 
#   geom_line(aes(x = question, y = time, group = ResponseId)) +
#   facet_wrap(~ResponseId) + 
#   geom_hline(aes(yintercept = mean), color = "blue")
```


## VISUALIZATIONS

```{r Confidence Interval Adjusted Plots}
data.identCurVal.means <- data.identCurVal.means %>% 
  mutate(meanTimeAdjBand = time - (data.identCurVal.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
  mutate(meanTimeAdjColor = time - (data.identCurVal.means %>% filter(graph == "Control Color") 
                                    %>% pull(time))) %>% 
  mutate(task = "Ident. Current Value")

data.identTrend.means <- data.identTrend.means %>% 
  mutate(meanTimeAdjBand = time - (data.identTrend.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
  mutate(meanTimeAdjColor = time - (data.identTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
  mutate(task = "Ident. Trend")

data.estCurVal.means <- data.estCurVal.means %>% 
  mutate(meanTimeAdjBand = time - (data.estCurVal.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
  mutate(meanTimeAdjColor = time - (data.estCurVal.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
  mutate(task = "Lookup Current Value")

data.estTrend.means <- data.estTrend.means %>% 
  mutate(meanTimeAdjBand = time - (data.estTrend.means %>% filter(graph == "Control Band") %>% pull(time))) %>% 
  mutate(meanTimeAdjColor = time - (data.estTrend.means %>% filter(graph == "Control Color") %>% pull(time))) %>% 
  mutate(task = "Lookup Trend")

means <- bind_rows(data.identCurVal.means, data.identTrend.means,
                   data.estCurVal.means, data.estTrend.means) %>% 
  mutate(task = factor(task, levels = c("Ident. Current Value", "Ident. Trend",
                       "Lookup Current Value","Lookup Trend"), ordered = T),
         label = graph,
         label = fct_recode(label, 
                            "Int. Size Band" = "IntSize Band", "Int. Size Color" = "IntSize Color",
                            "Sep. Size Band" = "SepSize Band", "Sep. Size Color" = "SepSize Color"),
         label = factor(label, levels = rev(c("Control Band", "Control Color", 
                            "Int. Size Band", "Int. Size Color", 
                            "Sep. Size Band", "Sep. Size Color")),
                        ordered =T))

ggplot(means, aes(x=label, y=meanTimeAdjBand)) +
  geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
  geom_hline(data = means %>% filter(graph == "Control Band"), 
             aes(yintercept = meanTimeAdjBand + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_hline(data = means %>% filter(graph == "Control Band"),
             aes(yintercept = meanTimeAdjBand - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_errorbar(width=0, aes(ymin=meanTimeAdjBand-ci, ymax=meanTimeAdjBand+ci, color = task), show.legend = F,
                linewidth = 1.6) +
  geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
  scale_y_continuous(limits = c(-5.5, 2), expand = expansion(mult = c(0, 0)), name = "Normalized Mean Time") +
  scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
  theme_minimal() +
  coord_flip() +
  facet_grid(rows = vars(task)) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.2)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
                                   size = rel(1.2)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10),
        panel.spacing = unit(30, "pt"))

ggsave("GraphComparativeCIs.svg", width=7, height=7.3)
ggsave("GraphComparativeCIs.png", width=7, height=7.3, bg = "white")

ggplot(means %>% filter(str_detect(graph, "Band")), aes(x=label, y=meanTimeAdjBand)) +
  geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
  geom_hline(data = means %>% filter(str_detect(graph, "Band")) %>% filter(graph == "Control Band"), 
             aes(yintercept = meanTimeAdjBand + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_hline(data = means %>% filter(str_detect(graph, "Band")) %>% filter(graph == "Control Band"),
             aes(yintercept = meanTimeAdjBand - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_errorbar(width=0, aes(ymin=meanTimeAdjBand-ci, ymax=meanTimeAdjBand+ci, color = task), show.legend = F,
                linewidth = 1.6) +
  geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
  scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
  scale_y_continuous(limits = c(-6, 6), expand = expansion(mult = c(0, 0)), name = "Normalized Mean Time") +
  theme_minimal() +
  coord_flip() +
  facet_grid(rows = vars(task)) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10))

ggsave("GraphComparativeCIs_Band.svg", width=7, height=3.65)
ggsave("GraphComparativeCIs_Band.png", width=7, height=3.65, bg = "white")

ggplot(data = means %>% filter(str_detect(graph, "Color")),
       aes(x=label, y=meanTimeAdjColor)) +
  geom_hline(yintercept = 0, linewidth = 0.3, color = "gray50") +
  geom_hline(data = means %>% filter(str_detect(graph, "Color")) %>% filter(graph == "Control Color"), 
             aes(yintercept = meanTimeAdjColor + ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_hline(data = means %>% filter(str_detect(graph, "Color")) %>% filter(graph == "Control Color"),
             aes(yintercept = meanTimeAdjColor - ci), linewidth = 0.4, color = "gray75", linetype = 2) +
  geom_errorbar(width=0, aes(ymin=meanTimeAdjColor-ci, ymax=meanTimeAdjColor+ci, color = task), show.legend = F,
                linewidth = 1.6) +
  geom_point(aes(color = task), shape=21, size=3.6, fill="white", show.legend = F) + 
  scale_color_manual(values = c("#317F9B","#13B6B9","#5F51B8","#9990E0","#AA4B53","#E2923C")) +
  scale_y_continuous(limits = c(-6, 6), expand = expansion(mult = c(0, 0)), 
                     name = "Normalized Mean Time") +
  theme_minimal() +
  coord_flip() +
  facet_grid(rows = vars(task)) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10))

ggsave("GraphComparativeCIs_Color.svg", width=7, height=3.65)
ggsave("GraphComparativeCIs_Color.png", width=7, height=3.65, bg = "white")
```

```{r}
nrow(data.participant %>% distinct(ResponseId))

data.participant.error <- data.participant %>% 
  mutate(ans = factor(ans_TF),
         label = graph,
         label = fct_recode(label, 
                            "Int. Size Band" = "IntSize Band", "Int. Size Color" = "IntSize Color",
                            "Sep. Size Band" = "SepSize Band", "Sep. Size Color" = "SepSize Color"),
         label = factor(label, levels = rev(c("Control Band", "Control Color", 
                            "Int. Size Band", "Int. Size Color", 
                            "Sep. Size Band", "Sep. Size Color"))),
         task = fct_recode(task, 
                           "Ident. Current Value" = "identCurVal",
                           "Ident. Trend" = "identTrend",
                           "Lookup Current Value" = "estCurVal",
                           "Lookup Trend" = "estTrend"),
         task = factor(task, levels = c("Ident. Current Value", "Ident. Trend",
                       "Lookup Current Value","Lookup Trend"), ordered = T))

ggplot(data = data.participant.error) + 
  geom_bar(aes(x = label, group = ans, fill = ans), position = position_stack()) + 
  geom_text(data = data.participant.error %>% filter(ans == T),
            aes(x = label, group = ans, label = ..count..), stat = "count", 
            position = position_fill(vjust = 0.5), 
            size = 3, hjust = 0) + 
  scale_fill_manual(labels = c("Incorrect", "Correct"),
                    values = c("#EB919A", "#73BCE6"),
                    name = "Answer Type") +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0)),
                     breaks = c(0,10,20,30,40,47),
                     labels = c("0","10","20","30","40","47"),
                     name = "Number of Errors") +
  scale_x_discrete(expand = expansion(mult = c(0.12, 0))) +
  coord_flip() + 
  facet_grid(rows = vars(task)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 0, l = 0)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10),
        panel.spacing = unit(12, "pt"),
        legend.position = "bottom")

ggsave("GraphComparativeErrors.svg", width=5, height=10)
ggsave("GraphComparativeErrors.png", width=5, height=10, bg = "white")
```



```{r Error plots v2}
data.participant.error.summarize <- data.participant.error %>% 
  group_by(task, label, ans) %>% 
  count() %>% 
  ungroup() %>% 
  complete(task, label, ans, fill = list(n = 0))

ggplot(data = data.participant.error.summarize %>% filter(ans == F)) + 
  geom_col(aes(x = label, y = n), fill = "#EB919A") + 
  geom_text(aes(x = label, y = n, label =  n), 
            size = 4, hjust = -0.7) + 
  # scale_fill_manual(labels = c("Incorrect", "Correct"),
  #                   values = c("#EB919A", "#73BCE6"),
  #                   name = "Answer Type") +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0)),
                     breaks = c(0,10,20,30,40,47),
                     labels = c("0","10","20","30","40","47"),
                     name = "Number of Errors",
                     limits = c(0,47)) +
  scale_x_discrete(expand = expansion(mult = c(0.12, 0))) +
  coord_flip() + 
  facet_grid(rows = vars(task)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 0),
                                   size = rel(1.2)),
        axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 0, l = 0),
                                   size = rel(1.2)),
        plot.margin = margin(t = 10,
                             r = 10, 
                             b = 10,
                             l = 10),
        legend.position = "bottom",
        panel.spacing = unit(30, "pt"),
        strip.text.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())

ggsave("GraphComparativeErrors_v2.svg", width=2.5, height=7.3)
ggsave("GraphComparativeErrors_v2.png", width=5, height=10, bg = "white")
```

```{r Likert Plot}
data.clean.likert.summarized <- data.clean.likert.factor %>% 
  group_by(label) %>% 
  count(likert) %>% 
  mutate(percent = n/47)

ggplot(data = data.clean.likert.summarized, 
       aes(x = label, y = percent, fill = reorder(likert, desc(likert)),
               group = reorder(likert, desc(likert)))) + 
  geom_col(width = 0.7, position = "fill") +
  geom_text(aes(label = n),
            color = ifelse((data.clean.likert.summarized$likert == "1" | data.clean.likert.summarized$likert == "5"),
                           "white", "black"),
            position = position_fill(vjust = 0.5), 
            size = 4) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0)),
                   breaks = c(seq(0, 1, by = .2)),
                   limits = c(0,1),
                   labels = scales::label_percent(),
                   name = "% of Responses") + 
  scale_x_discrete(expand = expansion(mult = c(0, 0)), limits = rev) + 
  scale_fill_manual(values = rev(brewer.pal(5, "RdYlBu")),
                    labels = rev(c("Very difficult", "Somewhat difficult",
                        "Neither easy nor difficult", "Somewhat easy", "Very easy")),
                    name = "Likert Rating") + 
  coord_flip() + 
  theme_minimal() + 
  guides(color = guide_legend(reverse=T)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0),
                                   size = rel(1.2)),
        axis.text.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.5)),
        legend.text = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0),
                                   size = rel(1.2)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0),
                                   size = rel(1.4)),
        aspect.ratio = 1/2.5,
        plot.margin = margin(t = 0,
                             r = 20, 
                             b = 15,
                             l = 10),
        legend.position = "bottom")

ggsave("GraphComparativeLikert.svg", width=10, height=5)
ggsave("GraphComparativeLikert.png", width=10, height=5, bg = "white")
```

